---
title: "modeling outcome with radiomic and clinical features"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">
.figure {
   margin-top: 25px;
   margin-bottom: 10px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      # fig.width = 7, fig.height = 5, 
                      fig.align='center'#, fig.show='hold'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

<style>
div.blue { background-color:#FF9966; border-radius: 5px; padding: 20px; font-size: 38px}
</style>
<div class = "blue">

<span style="color: white;">Recurrence prediction</span>

</div>
<br>

```{r library}
library(tidyverse)
library(tidymodels)
# library(dotwhisker)  # for visualizing regression results
library(themis)
library(gtsummary)
library(gplots)
library(ggcorrplot)
library(survival)
library(rpart.plot)
library(rattle)
library(xgboost)
library(kknn)
library(vip) 
```


```{r load}
clinical_ml <- read_rds("/Users/colinccm/Documents/GitHub/Peres/MilesForMoffittRadiomics/clinical.rds") %>% 
  select(-c(w_wo_contrast,
            gender, race, ethnicity, 
            baseline_ctscan_outside_moffitt, tumor_sequence_number, 
            "histology", tnm_edition_number_must_use, grade_differentiation,
         date_of_birth, any_unclassified_brca_mutation,
         comment_for_cardiac_comorbidity,
         vital_date_new, date_of_last_followup, fwdate_most_recent,
         germline_brca1_mutation, germline_brca2_mutation, somatic_brca1_mutation, ##### To add
         somatic_brca2_mutation, any_unclassified_brca_mutation,
         "hypertension", "diabetes_mellitus", "hypercholesterolemia",
         "chronic_kidney_disease", "cardiac_conditions_including_bu",
         comment_for_cardiac_comorbidity,
         "complete",
         ecog_posttrt, ecog_recurr, "ecog_pretrt_date", "ecog_posttrt_date", "ecog_recurr_date",
         contrast_enhancement, # What is the difference with w_w...
         age_at_Dx,
         
         months_at_first_neoadjuvant_chem, months_at_first_adjuvant_chem, months_at_first_chemo,
         months_at_first_surgery, age_at_surgery, age_at_first_recurrence, month_at_first_recurrence_Dx,
         months_at_surg_followup, months_at_neo_followup, months_at_chem_followup, months_of_surg_rec_free,
         months_of_neo_rec_free, months_of_chem_rec_free,
         months_of_dx_rec_free, months_of_treat_rec_free,
         has_the_patient_recurredafter_surg
  )) %>% 
  
  select(-c( # Include as year, month?
    date_of_diagnosis, baseline_ct_scan_date,
            date_of_first_neoadjuvant_chemot,
            date_of_first_surgery, date_of_first_adjuvant_chemother,
            "date_of_first_recurrence", "date_of_surgery_abstracted",
    first_treatment_date, first_chemo_date, "months_at_first_treatment", "rec_event_date",
    "months_at_treat_followup", "recurrence_date_after_surgery"
            ))

concordance <- read_rds("/Users/colinccm/Documents/GitHub/Peres/MilesForMoffittRadiomics/concordance.rds") %>% 
  filter(value_CCC >= 0.95) %>% 
  select(name) %>% 
  mutate(stable_features = str_match(name, "([a-z][:digit:]*)_*")[,2])

stable_features <- paste0(paste(#"nor_", 
                                concordance$stable_features, "[a-z]", sep = ""), collapse = "|")

mldata <- read_rds("/Users/colinccm/Documents/GitHub/Peres/MilesForMoffittRadiomics/radiomics.rds") %>% 
  select(mrn, contrastenhancementyn, matches(stable_features)) %>% 
  right_join(., clinical_ml %>% 
  select(-c(vital_new, 
         os_time, os_event,
         rec_event, recurrence_time)),
             by = "mrn") %>% 
  filter(!is.na(.[2]))

clinical_ml <- clinical_ml %>% 
  filter(str_detect(mrn, paste(mldata$mrn, collapse = "|")))
```

<br>

***

# `r emo::ji("memo")` Cohort

From 451 clinical info,  
 - 4 were removed for being grade_differentiation == "Well Differentiated"  
 - 23 were removed for being treatment_type == "Chemo Only"  
 - 26 were removed for being treatment_type == "Surgery Only" (2 overlap with Well Differentiated)  
From 538 radiomics tumor info,  
 - 385 are biggest tumor
 - 344 patients are common with clinical data (aka -19 chemo only, -20 surg only, -3 well diff ; 1 is surg+well diff)  

**We have now 344 patients in our cohort.**  
<br>

***

# Data exploration
## Stydy population

<div class = "row">
<div class = "col-md-5">
```{r demo}
mldata %>% select(contrastenhancementyn) %>% 
  tbl_summary(type = list(contrastenhancementyn ~ "categorical"))

mldata %>%
  # full_join(., clinical_ml) %>% 
  select(age_at_diagnosis, tnm_cs_mixed_group_stage, treatment_type, raceeth) %>% 
  tbl_summary()
```
</div>

<div class = "col-md-7">
```{r}
p <- qplot(x =age_at_diagnosis, data=subset(clinical_ml,!is.na(age_at_diagnosis)),
           fill=..count.., geom="histogram", bins = 25) 
p + scale_fill_viridis_c(
  alpha = 1,
  begin = 0,
  end = 1,
  direction = 1,
  option = "A",
  values = NULL,
  space = "Lab",
  na.value = "grey50",
  guide = "colourbar",
  aesthetics = "fill"
) +
  theme_minimal(base_size = 16) +
  labs(x="Age at Diagnosis", y="Number of Patient", title="Repartition of Age at Diagnosis")
```
</div>
</div>

<br>

<div class = "row">
<div class = "col-md-5">
```{r}
mldata %>% 
  select(has_the_patient_recurred) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))
```
</div>

<div class = "col-md-7">
```{r}
mldata %>% 
  ggplot(aes(x= has_the_patient_recurred)) + 
  geom_bar(fill = "darkslategray")+
  coord_flip()+
  theme_minimal(base_size = 20)+
  labs(x = NULL)+
  ggtitle("Imbalanced data for recurrence outcome")
```
</div>
</div>

<br>
<br>


## Stable features

75 stable features were selected after concordance analysis with a concordance ≥ 0.95.

### Heatmap
```{r heatplot, fig.width=12}
df1 <- as.data.frame(mldata) %>% select(mrn, has_the_patient_recurred,
                                        tnm_cs_mixed_group_stage, raceeth,
                                        matches("^f[0-9]")) %>%
  distinct(mrn, .keep_all = TRUE) %>%
  # arrange(has_the_patient_recurred) %>%
  unite(mrn, c(mrn, has_the_patient_recurred, tnm_cs_mixed_group_stage, raceeth), sep = "_", remove = TRUE) %>%
  `row.names<-`(.$mrn) %>%
  select(-mrn)

# Create matrix and drop NA, scale on patient
df2 <- t(scale(t(as.matrix(df1)))) # scale for standardizing the data to make variables comparable
# df2 <- df2[complete.cases(df2 * 0), , drop=FALSE]

# Create colors for cluster
condition_colors <- unlist(lapply(rownames(df2), function(x){
  if(grepl("No Recurrence", x)) "grey"
  else if(grepl("Recurrence", x)) "pink"
}))

condition_colors1 <- unlist(lapply(rownames(df2), function(x){
  case_when(
    str_detect(x, "1") ~ "steelblue1",
    str_detect(x, "2") ~ "black",
    str_detect(x, "3") ~ "tan1",
    str_detect(x, "4") ~ "orange",
    TRUE          ~ NA_character_)
}))

condition_colors2 <- unlist(lapply(rownames(df2), function(x){
  case_when(
    str_detect(x, "White") ~ "#03051AFF",
    str_detect(x, "Black") ~ "red",
    str_detect(x, "Hispanic") ~ "blue",
    str_detect(x, "Other") ~ "darkgrey")
}))


mycols <- cbind(condition_colors, condition_colors1)

# Transpose
df2 <- t(df2)

heatmap.2(df2, #main = "kjh",
          trace = "none", density="none", col=bluered(20), cexRow=1,
          lwid=c(1.2, 10), # decrease width of left dendro
          # lhei=c(1.1, 10),
          margins = c(1,10), # bottom, right
          ColSideColors = condition_colors,
          scale = "none",
          # Colv = FALSE,
          key.par=list(mgp=c(1.5, 0.5, 0), # pos for value, number, axes
                       mar=c(3.5, 1, 2.5, 1) # color key pos down, left, top, right
                       )
          )
legend(0.78, 0.95, # right, up
       legend = c("Recurrence", "No Recurrence"), fill = c("pink", "grey"), cex = 0.6,
       bty = "n")

# heatmap.plus(df2,
#              col = bluered(20),
#              cexRow = 1,
#              margins = c(1, 10),
#              # bottom, right
#              ColSideColors = mycols,
#              scale = "none"
# )
# legend(0.78, 0.95, # right, up
#        legend = c("Recurrence", "No Recurrence"), fill = c("pink", "grey"), cex = 0.6,
#        bty = "n")
```
<br>
<br>

### Correlation

```{r, fig.height=12, fig.width=12}
a <- mldata %>% select(matches("^f[0-9]"))
p.mat <- cor_pmat(a)
mat <- cor(a, use = "pairwise.complete.obs")
ggcorrplot(mat, hc.order = TRUE, method = "square",
           # p.mat = p.mat, # Barring the no significant coefficient
           insig = "blank", # Leave blank on no significant coefficient
           type = "lower",
           # lab = TRUE,
           title = "Correlation between radiomics features",
           show.legend = TRUE, legend.title = "Correlation", show.diag = TRUE,
           # lab_col = "darkblue", lab_size = 3,
           sig.level = 0.05, #insig = c("pch", "blank"), pch = 4, pch.col = "black", pch.cex = 10,
           tl.cex = 10,
           tl.srt = 90,
           # digits = 1,
           outline.color = "white",
  ggtheme = ggplot2::theme_gray,
  colors = c("blue", "white", "#E46726")#6D9EC1
)
```
<br>
<br>

***

## Impact of features on HR

### Features by outcome status
```{r}
rec_data <- mldata %>%
  left_join(., clinical_ml %>% select(mrn, rec_event, recurrence_time))

rec_data %>% select(matches("^f[0-9]"), has_the_patient_recurred) %>%
  tbl_summary(by = has_the_patient_recurred,
              sort = list(everything() ~ "frequency"),
              digits = list(everything() ~  2)) %>%
  bold_labels() %>% add_p() %>% bold_p(t = .05)
```

### HR of recurrence
```{r}
rec_data %>% select(matches("^f[0-9]"), rec_event, recurrence_time) %>%
  select(1:20, rec_event, recurrence_time) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = rec_data$recurrence_time,
                             event = rec_data$rec_event)),
                   exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()

rec_data %>% select(matches("^f[0-9]"), rec_event, recurrence_time) %>%
  select(21:40, rec_event, recurrence_time) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = rec_data$recurrence_time,
                             event = rec_data$rec_event)),
                   exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
rec_data %>% select(matches("^f[0-9]"), rec_event, recurrence_time) %>%
  select(41:60, rec_event, recurrence_time) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = rec_data$recurrence_time,
                             event = rec_data$rec_event)),
                   exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
rec_data %>% select(matches("^f[0-9]"), rec_event, recurrence_time) %>%
  select(60:ncol(.)) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = rec_data$recurrence_time,
                             event = rec_data$rec_event)),
                   exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
```
<br>

***

# Build a model
## Splitting the data

The data is split in 3/4 for training and testing for better robustness.  
A strata is applied to the split function to balance contrastenhancementyn in both sets.  
```{r}
# Explore what will need to be changed
skimr::skim(mldata)

set.seed(1234)

# 1. Splitting the data
# 3/4 of the data into the training set but split evenly winthin race
data_split <- initial_split(mldata, prop = 3/4, strata = contrastenhancementyn)
# Create training and testing datasets:
train_data <- training(data_split)
test_data  <- testing(data_split)
```

```{r demo split}
train_data %>% 
  mutate(set = "training") %>% 
  bind_rows(., test_data %>% 
  mutate(set = "testing")) %>% 
  select(has_the_patient_recurred, contrastenhancementyn, set) %>% 
  tbl_summary(by = set,
              type = list(contrastenhancementyn ~ "categorical")) %>% 
  add_p()
```
<br>

***

## Build a recipe

It is an imbalance between Recurrence and no recurrence cases, the models use `step_smote` to balance the cases in the training data.  
It use nearest neighbor to create new synthetic observation almost similar.  
To increase accuracy, I used tuning function to select the best number of tree, number of node, sample_size, penalty,, etc... and avoid bias decision.
I used a 10 fold cross validation for the tuning for better tuning. It evaluate metrics like accuracy and roc_auc 10 times on a different split of the training set.
A strata is again applied to the cross validation sets to balance contrastenhancementyn.  

```{r recipe}
# 2. Data pre processing and features engineering + imputation
# Recipe
mldata_recipe <-
  # 1.model formula
  recipe(has_the_patient_recurred ~ ., data = train_data)  %>% 
  # 2.keep these variables but not use them as either outcomes or predictors
  update_role(mrn, new_role = "ID") %>%
  update_role(contrastenhancementyn, new_role = "strata") %>% 
  # remove variables that contain only a single value.
  step_zv(all_predictors()) %>% # or step_nzv
  # 3.If factor with too much levels, collapse lower levels
  # step_other(Histology, threshold = 0.05) %>% 
  # data_recipe %>% prep() %>% juice() %>% count(Histology)
  
  step_novel(all_nominal(), -all_outcomes()) %>% # Create a previously unseen factor level to a new value.

  # 4.Imputation
  step_unknown(all_nominal_predictors()) %>% 
  step_impute_median(all_numeric_predictors()) %>%
  # 5.change all factor to indicator/dummy variables for model that cannot handle factor variables
  step_dummy(all_nominal_predictors()) %>%
  
  # step_normalize(all_predictors(), -all_nominal()) %>%  # Normalize numeric value, important for glmnet

  # Feature engineering on dates
  # step_date(all_of(meaningful_dates), features = c("year", "month")) %>% 
  # step_rm(meaningful_dates)
  
  # LAST.For imbalance, model memorize the few example and
  step_smote(has_the_patient_recurred) # Use nearest neighbor to create new synthetic observation almost similar


set.seed(456)
# 10 fold cross validation
mldata_folds <- vfold_cv(train_data, strata = contrastenhancementyn)
```
<br>

***

# DECISION TREE
```{r decision_tree}
tree_spec <- decision_tree(
  cost_complexity = tune(),
  tree_depth = tune(),
  min_n = tune()) %>% 
  set_engine("rpart") %>% 
  set_mode("classification")

tree_workflow <- 
  workflow() %>% 
  add_recipe(mldata_recipe) %>% 
  add_model(tree_spec) 

tree_grid <- grid_regular(cost_complexity(),
                          tree_depth(),
                          min_n(), levels = 4)

doParallel::registerDoParallel()
set.seed(789)
tree_tune <- tree_workflow %>% 
  tune_grid(
    resamples = mldata_folds,
    grid = tree_grid,
    metrics = metric_set(roc_auc, accuracy, sensitivity, specificity)
  )
# Explore tuning
autoplot(tree_tune) + theme_light()



# tree_tune %>% 
#   collect_metrics() %>% 
#   filter(.metric == "accuracy" | .metric == "roc_auc") %>% 
#   filter(min_n == 40 & tree_depth == 10) %>% 
#   select(mean, cost_complexity,tree_depth, .metric) %>% 
#   # pivot_longer(cost_complexity:tree_depth,
#   #              values_to = "value",
#   #              names_to = "param") %>% 
#   ggplot(aes(cost_complexity, mean)) +
#   geom_point(show.legend = FALSE) +
#   # facet_wrap( . ~ param, scales = "free_x") %>% 
#   facet_grid( . ~ .metric)
set.seed(789)
final_tree <- tree_workflow %>% 
  finalize_workflow(select_best(tree_tune, "accuracy"))
final_tree
set.seed(789)
tree_final_fit <- fit(final_tree, data = train_data)
tree_final_fit
```


```{r plot decision_tree, fig.width=12}
tree_final_fit %>%
  extract_fit_engine() %>%
  rpart.plot()

# cart_spec <-
#    decision_tree(
#      cost_complexity = 1e-10,
#   tree_depth = 1,
#   min_n = 2
#    ) %>%
#    set_engine("rpart") %>%
#    set_mode("classification")
# 
# set.seed(789)
# cart_fit <- 
#    cart_spec %>%
#    fit(has_the_patient_recurred ~ ., data = train_data)
# cart_fit <- repair_call(cart_fit, data = train_data)

# fancyRpartPlot(cart_fit$fit)
```

## KM by risk group
```{r}
# mysurv <- Surv(rec_data$recurrence_time, event = rec_data$rec_event)
# myplot <- survfit(mysurv~risk_group, data = rec_data)
# myplot <- ggsurvplot(myplot, data = rec_data,
#            title = "Recurrence Analysis",
#            font.main = c(24, "bold", "black"),
#            font.x = c(20, "bold", "black"),
#            font.y = c(20, "bold", "black"),
#            font.legend = c(20, "bold", "black"),
#            font.tickslab = c(18, "bold", "black"),
#            size = 1.5,
#            
#            xlab = "Time in months", 
#            legend = "top",
#            legend.title = "",
#            # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
#            # palette = c("#03051AFF", "blue", "red"),
#            pval = TRUE,
#            pval.coord = c(0, 0.1),
#            conf.int = FALSE,
#            xlim = c(0, 400),
#            # Censor
#            censor = TRUE
# ) + guides(colour = guide_legend(nrow = 3))
```
<br>

***

# XGBOOST
```{r xgboost}
############################################################################################### xgboost----
# xgboost_recipe <- 
#   recipe(formula = has_the_patient_recurred ~ ., data = train_data) %>% 
#   step_novel(all_nominal(), -all_outcomes()) %>% 
#   step_dummy(all_nominal(), -all_outcomes(), one_hot = TRUE) %>% 
#   step_zv(all_predictors()) 
xgboost_spec <- 
  boost_tree(trees = tune(), min_n = tune(), tree_depth = tune(), learn_rate = tune(), 
             loss_reduction = tune(), sample_size = tune()) %>% 
  set_mode("classification") %>% 
  set_engine("xgboost") 

xgboost_workflow <- 
  workflow() %>% 
  add_recipe(mldata_recipe) %>% 
  add_model(xgboost_spec) 

set.seed(789)
xgboost_tune <-
  tune_grid(xgboost_workflow, resamples = mldata_folds, grid = 10)

######################################################################### Explore xgboost Tuning Results ----

# Visualize tuned parameters
autoplot(xgboost_tune)
# mtry is the number of predictor randomly selected -> needs to be 
# mim_n is the minimal node size -> needs to be small

# xgboost_tune %>% 
#   collect_metrics() %>% 
#   filter(.metric == "accuracy") %>% 
#   select(mean, trees:sample_size) %>% 
#   pivot_longer(trees:sample_size,
#                values_to = "value",
#                names_to = "param") %>% 
#   ggplot(aes(value, mean, color = param)) +
#   geom_point(show.legend = FALSE) +
#   facet_wrap( . ~ param, scales = "free_x")
# 
# xgboost_tune %>% 
#   collect_metrics() %>% 
#   filter(.metric == "roc_auc") %>% 
#   select(mean, trees:sample_size) %>% 
#   pivot_longer(trees:sample_size,
#                values_to = "value",
#                names_to = "param") %>% 
#   ggplot(aes(value, mean, color = param)) +
#   geom_point(show.legend = FALSE) +
#   facet_wrap( . ~ param, scales = "free_x")
set.seed(789)

final_xgboost <- xgboost_workflow %>% 
  finalize_workflow(select_best(xgboost_tune, "roc_auc"))
final_xgboost
```
<br>

***

# RANDOM FOREST
```{r rand_forest}
############################################################################################### Random FOREST ----
set.seed(789)
# Model specification
ranger_spec <- rand_forest(
  # tune right value for the number of predictors that will be randomly sampled at each split when creating the tree models
  mtry = tune(), 
  # tune right value for the minimum number of data points in a node that are required for the node to be split further.
  min_n = tune(),
  trees = 1000) %>% 
  set_mode("classification") %>% 
  set_engine("ranger")

# Set up a work flow
ranger_workflow <- 
  workflow() %>% 
  # Add preprocessor
  add_recipe(mldata_recipe) %>% # here is an unfit mode
  add_model(ranger_spec) # add our model specification

# Tuning
doParallel::registerDoParallel()
set.seed(789)
# will tune mtry and min_m on a grid
ranger_tune <-
  tune_grid(ranger_workflow, # Will take our workflow and apply it on
            resamples = mldata_folds, # each fold of the data for 
            grid = 20) # How many candidate point do I want to try
# Try the 20 point with each min_n and mtry
# Then train on analysis cv and assessed on the test of cv
# will compute performance matrix on each of these of the 20 candidate model

# May need to add specificity and sensitivity to metrics if we have rare events. these 2 will tell us how the model did for our positive and negative cases
# If sens is low it means the model had a really hard time finding the rare case (could mean step_smote is bad idea for this model)


############################################################################### II ### Explore Tuning Results ----

# Visualize tuned parameters
autoplot(ranger_tune)
# mtry is the number of predictor randomly selected -> needs to be 
# mim_n is the minimal node size -> needs to be small

# ranger_tune %>% 
#   collect_metrics() %>% 
#   filter(.metric == "roc_auc") %>% 
#   select(mean, min_n, mtry) %>% 
#   pivot_longer(min_n:mtry,
#                values_to = "value",
#                names_to = "param") %>% 
#   ggplot(aes(value, mean, color = param)) +
#   geom_point(show.legend = FALSE) +
#   facet_wrap( . ~ param, scales = "free_x")


# # Tune more?
# # Can make a regular grid
# new_grid <- grid_regular(
#   mtry(range = c(25, 75)),
#   min_n(range = c(0, 25)),
#   levels = 10
# )
# 
# set.seed(123)
# sec_tune_results <- tune_grid( # will tune mtry and min_m on a grid
#   tune_wf, # tune worflow
#   resamples = data_folds, # on this data
#   grid = new_grid
# )
# 
# sec_tune_results %>% collect_metrics() %>% 
#   filter(.metric == "roc_auc") %>% 
#   mutate(min_n = factor(min_n)) %>% 
#   ggplot(aes(mtry, mean, color = min_n)) +
#   geom_line(alpha = 0.5, size = 1.5) +
#   geom_point()

# Step Finalize the model with our tuned parameters
# best_auc <- select_best(ranger_tune, # or sec_tune_results if tuned more,
#                         "roc_auc")
# 
# final_rf <- finalize_model(ranger_spec,
#                            best_auc)
# # Aka same
# final_rf <- ranger_spec %>% 
#   finalize_model(select_best(ranger_tune, "accuracy"))
set.seed(789)

final_rf <- ranger_workflow %>% 
  finalize_workflow(select_best(ranger_tune, "accuracy"))
final_rf
```
<br>

***

# LOGISTIC REGRESSION
```{r logistic_reg}
# # Tune lambda
# 
# # logistic reg, choose regularized log reg with mixture 1 for Lasso model
# # Because lots of var for few rows (samples) but don't know which vars are important
# 
# # Find the optimal value of lambda that minimizes the cross-validation error
# # Need to prep data differently
# train_data_lambda <- training(data_split) %>% 
#   drop_na() %>% select(-mrn)
# 
# # Dummy code categorical predictor variables
# x <- model.matrix(has_the_patient_recurred ~ .-contrastenhancementyn, data = train_data_lambda)[,-1]
# # Convert the outcome (class) to a numerical variable
# y <- ifelse(train_data_lambda$has_the_patient_recurred == "Recurrence", 1, 0)
# 
# library(glmnet)
# set.seed(123)
# cv.lasso <- cv.glmnet(x, y, alpha = 1, family = "binomial")
# plot(cv.lasso)
# # cv.lasso$lambda.min
# # # The left dashed vertical line indicates that the log of the optimal value of lambda is approximately -4, 
# # # which is the one that minimizes the prediction error. This lambda value will give the most accurate model.
# # cv.lasso$lambda.1se
# # # Fit the final model on the training data
# # model <- glmnet(x, y, alpha = 1, family = "binomial",
# #                 lambda = cv.lasso$lambda.min)
# # # Display regression coefficients
# # coef(model)



glmnet_spec <- 
  logistic_reg(penalty = tune(), mixture = tune()) %>% # Looks ridge would increase really slightly mixture = 0
  set_mode("classification") %>% 
  set_engine("glmnet") 

glmnet_workflow <- 
  workflow() %>% 
  add_recipe(mldata_recipe) %>% 
  add_model(glmnet_spec) 

glmnet_grid <- tidyr::crossing(penalty = 10^seq(-6, -1, length.out = 20), mixture = c(0, 0.05, 
                                                                                      0.2, 0.4, 0.6, 0.8, 1)) 
set.seed(789)
glmnet_tune <- 
  tune_grid(glmnet_workflow, resamples = mldata_folds, grid = glmnet_grid) 

# glmnet_tune <- tune_grid(glmnet_workflow, 
#             resamples = mldata_folds, 
#             grid = 20)
############################################################################### II ### Explore Tuning Results ----


# Visualize tuned parameters
autoplot(glmnet_tune)
# mtry is the number of predictor randomly selected -> needs to be 
# mim_n is the minimal node size -> needs to be small


# Step Finalize the model with our tuned parameters
# best_acc <- select_best(glmnet_tune, # or sec_tune_results if tuned more,
#                         "accuracy")
# 
# final_glmnet <- finalize_model(glmnet_spec,
#                                best_acc)
# # Aka same
# final_glmnet <- glmnet_spec %>% 
#   finalize_model(select_best(glmnet_tune, "roc_auc"))
set.seed(789)

final_glmnet <- glmnet_workflow %>% 
  finalize_workflow(select_best(glmnet_tune, "roc_auc")) 
final_glmnet
```
<br>

***

# KKNN

```{r}
kknn_spec <- 
  nearest_neighbor(neighbors = tune(), weight_func = tune()) %>% 
  set_mode("classification") %>% 
  set_engine("kknn") 

kknn_workflow <- 
  workflow() %>% 
  add_recipe(mldata_recipe) %>% 
  add_model(kknn_spec) 

set.seed(789)
kknn_tune <-
  tune_grid(kknn_workflow, 
            resamples = mldata_folds, 20)

autoplot(kknn_tune)
set.seed(789)

final_kknn <- kknn_workflow %>% 
  finalize_workflow(select_best(kknn_tune, "accuracy"))
final_kknn
```


```{r Performance Metrics}
################################################################### Calculate Performance Metrics with tuned model
set.seed(789)

tree_results <- final_tree %>% 
  fit_resamples(
    resamples = mldata_folds,
    metrics = metric_set(roc_auc, accuracy, sensitivity, specificity),
    control = control_resamples(save_pred = TRUE)
  )

set.seed(789)
xgboost_results <- final_xgboost %>% 
  fit_resamples(
    resamples = mldata_folds,
    metrics = metric_set(roc_auc, accuracy, sensitivity, specificity),
    control = control_resamples(save_pred = TRUE)
  )

set.seed(789)
rf_results <- final_rf %>% 
  fit_resamples( # is not doing any tuning, measuring performance on cross validation data
    resamples = mldata_folds,
    metrics = metric_set(roc_auc, accuracy, sensitivity, specificity),
    control = control_resamples(save_pred = TRUE, verbose = TRUE)
  )

set.seed(789)
glmnet_results <- final_glmnet %>% 
  fit_resamples(
    resamples = mldata_folds,
    metrics = metric_set(roc_auc, accuracy, sensitivity, specificity),
    control = control_resamples(save_pred = TRUE)
  )

set.seed(789)
kknn_results <- final_kknn %>% 
  fit_resamples(
    resamples = mldata_folds,
    metrics = metric_set(roc_auc, accuracy, sensitivity, specificity),
    control = control_resamples(save_pred = TRUE)
  )

###############################################################################  Support vector machine # not necessary
###############################################################################  neural network
```
<br>

***

# Evaluate models
```{r evaluate models}
# Explore Performance Metrics
# collect_metrics(xgboost_results)
# collect_metrics(tree_results)
# collect_metrics(rf_results)
# collect_metrics(glmnet_results)
# Accuracy is llow
# Sensitivity has 50% chance finding the minority class pop

# xgboost_results %>% 
#   collect_predictions() %>% 
#   group_by(id) %>% 
#   roc_curve(has_the_patient_recurred, .pred_Recurrence) %>% 
#   autoplot()
# tree_results %>% 
#   collect_predictions() %>% 
#   group_by(id) %>% 
#   roc_curve(has_the_patient_recurred, .pred_Recurrence) %>% 
#   autoplot()
# rf_results %>% 
#   collect_predictions() %>% 
#   group_by(id) %>% 
#   roc_curve(has_the_patient_recurred, .pred_Recurrence) %>% 
#   autoplot()
# glmnet_results %>% 
#   collect_predictions() %>% 
#   group_by(id) %>% 
#   roc_curve(has_the_patient_recurred, .pred_Recurrence) %>% 
#   autoplot()

rf_results %>% # Compare both models
  collect_predictions() %>% 
  mutate(model = "rf") %>% 
  bind_rows(glmnet_results %>% 
              collect_predictions() %>% 
              mutate(model = "glmet")) %>% 
  bind_rows(xgboost_results %>% 
              collect_predictions() %>% 
              mutate(model = "xgboost")) %>% 
  bind_rows(tree_results %>% 
              collect_predictions() %>% 
              mutate(model = "tree")) %>% 
  bind_rows(kknn_results %>% 
              collect_predictions() %>% 
              mutate(model = "kknn")) %>% 
  group_by(model) %>% 
  roc_curve(has_the_patient_recurred, .pred_Recurrence) %>% 
  autoplot()

rf_results %>% # Compare both models
  collect_metrics() %>% 
  select(".metric", rf_mean = mean) %>% 
  full_join(., glmnet_results %>% 
              collect_metrics() %>% 
              select(".metric", glmet_mean = mean)
            , by = ".metric") %>% 
  full_join(., xgboost_results %>% 
              collect_metrics() %>% 
              select(".metric", xgboost_mean = mean)
            , by = ".metric") %>% 
  full_join(., tree_results %>% 
              collect_metrics() %>% 
              select(".metric", tree_mean = mean)
            , by = ".metric") %>% 
  full_join(., kknn_results %>% 
              collect_metrics() %>% 
              select(".metric", kknn_mean = mean)
            , by = ".metric")

rf_results %>% # Compare both models
  collect_metrics() %>% 
  mutate(model = "rf") %>% 
  bind_rows(glmnet_results %>% 
              collect_metrics() %>% 
              mutate(model = "glmet")) %>% 
  bind_rows(xgboost_results %>% 
              collect_metrics() %>% 
              mutate(model = "xgboost")) %>% 
  bind_rows(tree_results %>% 
              collect_metrics() %>% 
              mutate(model = "tree")) %>% 
  bind_rows(kknn_results %>% 
              collect_metrics() %>% 
              mutate(model = "kknn")) %>% 
  
  ggplot(aes(x= .metric, y=mean, fill = model))+
  geom_bar(stat = "identity",
           position = position_dodge())+
  geom_errorbar(aes(x = .metric,
                    ymin = mean - std_err,
                    ymax = mean + std_err),
                width = 0.2, alpha = 0.5,
                position=position_dodge(width=0.9))+
  theme_minimal()+
  scale_fill_viridis_d(option = "A")
```
<br>
<br>

**Random forest and logistic regression are investigated deeper due to their respectivive higher accuracy and specificity results**

<br>

```{r evaluate models2}
# xgboost_results %>% 
#   conf_mat_resampled()
# tree_results %>% 
#   conf_mat_resampled()
tree_results %>% 
  conf_mat_resampled()
glmnet_results %>% 
  conf_mat_resampled()

# Visualization
# xgboost_results %>% # is the saved predictions
#   collect_predictions() %>% 
#   conf_mat(truth = has_the_patient_recurred, estimate = .pred_class) %>% 
#   autoplot()
# tree_results %>% 
#   collect_predictions() %>% 
#   conf_mat(truth = has_the_patient_recurred, estimate = .pred_class) %>% 
#   autoplot()
tree_results %>% # is the saved predictions
  collect_predictions() %>% 
  conf_mat(truth = has_the_patient_recurred, estimate = .pred_class) %>% 
  autoplot()+
  ggtitle("Decision tree")
glmnet_results %>% 
  collect_predictions() %>% 
  conf_mat(truth = has_the_patient_recurred, estimate = .pred_class) %>% 
  autoplot()+
  ggtitle("Logistic Regression")

# Calculate prediction after the fact
# xgboost_results %>% collect_predictions() %>% 
#   ppv(truth = has_the_patient_recurred, estimate = .pred_class) # do histog
# tree_results %>% collect_predictions() %>% 
#   ppv(truth = has_the_patient_recurred, estimate = .pred_class)
# rf_results %>% collect_predictions() %>% 
#   ppv(truth = has_the_patient_recurred, estimate = .pred_class)
# glmnet_results %>% collect_predictions() %>% 
#   ppv(truth = has_the_patient_recurred, estimate = .pred_class)
```
<br>

***

# Features importance
```{r vip}

###################################### tree
# printcp(cart_fit)

###################################### Ranger
# Need to train the model one more time but without tuning to go faster
set.seed(789)
importance_spec <- ranger_spec %>% 
  finalize_model(select_best(ranger_tune, "roc_auc")) %>% 
  set_engine("ranger", importance = "permutation") # permutation based importance

# represents the mean decrease in node impurity (and not the mean decrease in accuracy)
workflow() %>% 
  add_recipe(mldata_recipe) %>% 
  add_model(importance_spec) %>% 
  fit(train_data) %>% 
  extract_fit_parsnip() %>% 
  vip(aesthetics = list(alpha = 0.5, fill = "midnightblue"),
      # geom = "point",
      num_features = 20
  ) +
  theme_minimal() + 
  ggtitle("Varaiable importance from Random forest model")


###################################### glmnet
# Need to train the model one more time but without tuning to go faster
set.seed(789)
importance_spec <- glmnet_spec %>% 
  finalize_model(select_best(glmnet_tune, "roc_auc")) %>% 
  set_engine("glmnet", importance = "permutation") # permutation based importance

# represents the mean decrease in node impurity (and not the mean decrease in accuracy)
workflow() %>% 
  add_recipe(mldata_recipe) %>% 
  add_model(importance_spec) %>% 
  fit(train_data) %>% 
  extract_fit_parsnip() %>% 
  vip(aesthetics = list(alpha = 0.5, fill = "midnightblue"),
      # geom = "point",
      num_features = 20
  ) +
  theme_minimal() +
  ggtitle("Varaiable importance from logistic regression model")
```
<br>

***

# Evaluate on the testing dataset
## Fit on testing using RF
### Compare testing performance vs training performance
```{r fit on testing RF}
############################################################################################### AT LAST
# Step finalize Fit : fitting to the whole training and evaluating on the testing data
# With the model of our choice
set.seed(789)
final_fit <- final_tree %>% 
  last_fit(data_split)

# Step Explore the model on testing set
# Collect metrics and compare number with the metrics from the training
# Can see if lower or higher...overfit our data, etc
collect_metrics(final_fit)
# Compare to the training previous number
collect_metrics(tree_results) 

collect_metrics(final_fit) %>% 
  mutate(set = "testing") %>% 
  rename(mean = .estimate) %>% 
  bind_rows(collect_metrics(rf_results) %>% 
              mutate(set = "training")) %>% 
  filter(str_detect(.metric, "accuracy|roc_auc")) %>% 
  ggplot(aes(x= .metric, y=mean, fill = set))+
  geom_bar(stat = "identity",
           position = position_dodge()) + 
  geom_errorbar(aes(x = .metric,
                    ymin = mean - std_err,
                    ymax = mean + std_err),
                width = 0.2, alpha = 0.5,
                position=position_dodge(width=0.9)) +
  theme_minimal()
```

### Predictions on testing set
```{r fit on testing}
final_fit %>% 
  collect_predictions() %>% 
  conf_mat(truth = has_the_patient_recurred, estimate = .pred_class)
final_fit %>% 
  collect_predictions() %>% 
  conf_mat(truth = has_the_patient_recurred, estimate = .pred_class) %>% 
  autoplot() +
  ggtitle("Tree model on testing data")
```
<br>

## Fit on testing using GLMNET
### Compare testing performance vs training performance
```{r}
# If choose glmnet, can see estimate on the testing
set.seed(789)
final_fit_sec <- final_glmnet %>% 
  last_fit(data_split)

collect_metrics(final_fit)
# Compare to the training previous number
collect_metrics(glmnet_results)

collect_metrics(final_fit) %>% 
  mutate(set = "testing") %>% 
  rename(mean = .estimate) %>% 
  bind_rows(collect_metrics(glmnet_results) %>% 
              mutate(set = "training")) %>% 
  filter(str_detect(.metric, "accuracy|roc_auc")) %>% 
  ggplot(aes(x= .metric, y=mean, fill = set))+
  geom_bar(stat = "identity",
           position = position_dodge()) + 
  geom_errorbar(aes(x = .metric,
                    ymin = mean - std_err,
                    ymax = mean + std_err),
                width = 0.2, alpha = 0.5,
                position=position_dodge(width=0.9)) +
  theme_minimal()
```

### Predictions on testing set
```{r, fig.height=15, fig.width=12}
final_fit_sec %>%
  pull(.workflow) %>% 
  pluck(1) %>% 
  tidy(exponentiate = TRUE) %>% 
  arrange(desc(abs(estimate))) %>%
  filter(abs(estimate) >0)
# kableExtra::kable(digits = 3)

final_fit_sec %>% # WARNING it uses the scaled data
  pull(.workflow) %>% 
  pluck(1) %>% 
  tidy() %>% 
  filter(term != "(Intercept)") %>% 
  arrange(desc(abs(estimate))) %>% 
  filter(abs(estimate) >0) %>% 
  ggplot(aes(estimate, fct_reorder(term, desc(estimate)), color = estimate > 0))+
  geom_vline(xintercept = 0, color = "lightgrey", lty = 2, size = 1.2) +
  geom_point() + 
  scale_color_discrete(name = "Feature Effect \non outcome", labels = c("Deleterious", "Beneficial")) +
  theme_minimal()+
  ggtitle("Meaningful Parameter Estimate Coefficients using logistic regression model")
```

### Compare both model performance on testing set

```{r}
final_fit_sec %>% collect_predictions() %>% 
  mutate(set = "tree") %>% 
  bind_rows(final_fit %>% collect_predictions() %>% 
              mutate(set = "rf")) %>% 
  group_by(set) %>% 
  summarize(recurrence = mean(.pred_Recurrence),
            no_recurrence = mean(`.pred_No Recurrence`)) %>% 
  ungroup() %>% 
  pivot_longer(cols = -set, names_to = "status", values_to = "probability") %>% 
  ggplot(aes(x= set, y=probability, fill = status))+
  geom_bar(stat = "identity",
           position = position_dodge()) +
  theme_minimal()


# final_fit_sec %>% collect_predictions() %>% 
#   mutate(set = "glmnet") %>% 
#   bind_rows(final_fit %>% collect_predictions() %>% 
#               mutate(set = "rf")) %>% 
#   mutate(is_predicton_correct = case_when(
#     has_the_patient_recurred == .pred_class     ~ "Cool!",
#     TRUE                                        ~ ":("
#   )) %>% 
#   group_by(set, is_predicton_correct) %>% 
#   summarize(recurrence = mean(.pred_Recurrence),
#             no_recurrence = mean(`.pred_No Recurrence`)) %>% 
#   ungroup() %>% 
#   pivot_longer(cols = -c(set, is_predicton_correct), names_to = "status", values_to = "probability") %>% 
#   ggplot(aes(x= is_predicton_correct, y=probability, fill = status))+
#   geom_bar(stat = "identity",
#            position = position_dodge()) + 
#   facet_wrap(. ~ set)



```
<br>

***

# Outcome Analysis

<!-- # logistic regression -->
```{r}
rec_data <- mldata %>% 
  left_join(., clinical_ml %>% select(mrn, rec_event, recurrence_time))
# 
# model <- glm(has_the_patient_recurred ~ treatment_type + age_at_diagnosis + raceeth + tnm_cs_mixed_group_stage + debulking_status, 
#              data = rec_data, family = binomial)
# tbl1 <- tbl_regression(model)
# tbl2 <- tbl_regression(model, exponentiate = TRUE)
# tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
```

## HR
```{r}
tbl1 <- rec_data %>% select(rec_event, recurrence_time,
                            raceeth, age_at_diagnosis, tnm_cs_mixed_group_stage, treatment_type,
                            f10statistical_, f81com_y_pxl, f9statistical_9,
                            f102avgcoocurre, f65flatness, f83com_x_mm, f87weighted_com) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = rec_data$recurrence_time,
                             event = rec_data$rec_event)),
                   exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()

tbl2 <- 
  coxph(Surv(time = rec_data$recurrence_time,
             event = rec_data$rec_event) ~ raceeth + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + f10statistical_ + f81com_y_pxl + f9statistical_9 + f102avgcoocurre + f65flatness + f83com_x_mm + f87weighted_com, data =  rec_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)

tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
<br>
<br>



***
***
***




<br>
<br>

<style>
div.blue { background-color:#FF9966; border-radius: 5px; padding: 20px; font-size: 38px}
</style>
<div class = "blue">

<span style="color: white;">Vital status prediction</span>

</div>
<br>
<br>

***

# Vital status

```{r os load}
# clinical_ml <- read_rds("/Users/colinccm/Documents/GitHub/Peres/MilesForMoffittRadiomics/clinical_ml.rds") %>% 
#   select(mrn, 
#          has_the_patient_recurred, vital_new,
#          rec_event, recurrence_time, os_event, os_time,
#          age_at_diagnosis, tnm_cs_mixed_group_stage, 
#          treatment_type, debulking_status,
#          raceeth)

mldata <- read_rds("/Users/colinccm/Documents/GitHub/Peres/MilesForMoffittRadiomics/radiomics.rds") %>% 
  select(mrn, contrastenhancementyn, matches(stable_features)) %>% 
  right_join(., clinical_ml %>% 
  select(-c(has_the_patient_recurred, rec_event, recurrence_time,
         os_event, os_time)),
             by = "mrn") %>% 
  filter(!is.na(.[2])) %>% 
  mutate(vital_new = factor(vital_new))

# clinical_ml <- clinical_ml %>% 
#   filter(str_detect(mrn, paste(mldata$mrn, collapse = "|")))
```



<br>

<div class = "row">
<div class = "col-md-5">
```{r}
mldata %>% 
  select(vital_new) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))
```
</div>

<div class = "col-md-7">
```{r}
mldata %>% 
  ggplot(aes(x= vital_new)) + 
  geom_bar(fill = "darkslateblue")+
  coord_flip()+
  theme_minimal(base_size = 20)+
  labs(x = NULL)+
  ggtitle("Imbalanced data for recurrence outcome")
```
</div>
</div>

<br>
<br>

***

# Impact of features on HR

## Features by outcome status
```{r}
os_data <- mldata %>% 
  left_join(., clinical_ml %>% 
  select(mrn, os_event, os_time), 
  by = "mrn")

os_data %>% select(matches("^f[0-9]"), vital_new) %>%
  tbl_summary(by = vital_new,
              sort = list(everything() ~ "frequency"),
              digits = list(everything() ~  2)) %>%
  bold_labels() %>% add_p() %>% bold_p(t = .05)
```

## HR of death
```{r}
os_data %>% select(matches("^f[0-9]"), os_event, os_time) %>%
  select(1:20, os_event, os_time) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = os_data$os_time,
                             event = os_data$os_event)),
                   exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()

os_data %>% select(matches("^f[0-9]"), os_event, os_time) %>%
  select(21:40, os_event, os_time) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = os_data$os_time,
                             event = os_data$os_event)),
                   exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
os_data %>% select(matches("^f[0-9]"), os_event, os_time) %>%
  select(41:60, os_event, os_time) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = os_data$os_time,
                             event = os_data$os_event)),
                   exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
os_data %>% select(matches("^f[0-9]"), os_event, os_time) %>%
  select(60:ncol(.)) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = os_data$os_time,
                             event = os_data$os_event)),
                   exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
```
<br>

***

# Build a model
## Splitting the data

The data is split in 3/4 for training and testing for better robustness.  
A strata is applied to the split function to balance contrastenhancementyn in both sets.  
```{r}
# Explore what will need to be changed
# skimr::skim(mldata)

set.seed(123)

# 1. Splitting the data
# 3/4 of the data into the training set but split evenly winthin race
data_split <- initial_split(mldata, prop = 3/4, strata = contrastenhancementyn)
# Create training and testing datasets:
train_data <- training(data_split)
test_data  <- testing(data_split)
```

```{r os demo split}
train_data %>% 
  mutate(set = "training") %>% 
  bind_rows(., test_data %>% 
  mutate(set = "testing")) %>% 
  select(vital_new, contrastenhancementyn, set) %>% 
  tbl_summary(by = set,
              type = list(contrastenhancementyn ~ "categorical")) %>% 
  add_p()
```
<br>

***

## Build a recipe

```{r}
# 2. Data pre processing and features engineering + imputation
# Recipe
mldata_recipe <-
  # 1.model formula
  recipe(vital_new ~ ., data = train_data)  %>% 
  # 2.keep these variables but not use them as either outcomes or predictors
  update_role(mrn, new_role = "ID") %>%
  update_role(contrastenhancementyn, new_role = "strata") %>% 

  step_zv(all_predictors()) %>% # or step_nzv
  step_novel(all_nominal(), -all_outcomes()) %>% # Create a previously unseen factor level to a new value.

  # 4.Imputation
  step_unknown(all_nominal_predictors()) %>% 
  step_impute_median(all_numeric_predictors()) %>%

  step_dummy(all_nominal_predictors()) %>%

  step_smote(vital_new) # Use nearest neighbor to create new synthetic observation almost similar

############################################################################### II ### Data Tuning ----
# train hyperparameter
set.seed(456)
# 10 fold cross validation
mldata_folds <- vfold_cv(train_data, strata = contrastenhancementyn)
```
<br>

***

# DECISION TREE
```{r os decision_tree}
set.seed(789)

# With workflow
tree_spec <- decision_tree(
  cost_complexity = tune(),
  tree_depth = tune(),
  min_n = tune()) %>% 
  set_engine("rpart") %>% 
  set_mode("classification")

tree_workflow <- 
  workflow() %>% 
  add_recipe(mldata_recipe) %>% 
  add_model(tree_spec) 

tree_grid <- grid_regular(cost_complexity(),
                          tree_depth(),
                          min_n(), levels = 4)

doParallel::registerDoParallel()
set.seed(789)
tree_tune <- tree_workflow %>% 
  tune_grid(
    resamples = mldata_folds,
    grid = tree_grid,
    metrics = metric_set(roc_auc, accuracy, sensitivity, specificity)
  )
# Explore tuning
autoplot(tree_tune) + theme_light()


final_tree <- tree_workflow %>% 
  finalize_workflow(select_best(tree_tune, "roc_auc")) # roc gas a nice curve
final_tree

set.seed(789)

tree_final_fit <- fit(final_tree, data = train_data)
tree_final_fit
```


```{r os plot decision_tree, fig.width=12}
tree_final_fit %>%
  extract_fit_engine() %>%
  rpart.plot()

cart_spec <-
   decision_tree(
  #    cost_complexity = 1e-10,
  # tree_depth = 10,
  # min_n = 40
   ) %>%
   set_engine("rpart") %>%
   set_mode("classification")

set.seed(789)
# cart_fit <- 
#    cart_spec %>%
#    fit(vital_new ~ .-mrn-contrastenhancementyn, data = train_data)
# cart_fit <- repair_call(cart_fit, data = train_data)

# fancyRpartPlot(cart_fit$fit)
```
<br>

***

# XGBOOST
```{r os xgboost}
############################################################################################### xgboost----
xgboost_spec <- 
  boost_tree(trees = tune(), min_n = tune(), tree_depth = tune(), learn_rate = tune(), 
             loss_reduction = tune(), sample_size = tune()) %>% 
  set_mode("classification") %>% 
  set_engine("xgboost") 

xgboost_workflow <- 
  workflow() %>% 
  add_recipe(mldata_recipe) %>% 
  add_model(xgboost_spec) 

set.seed(789)
xgboost_tune <-
  tune_grid(xgboost_workflow, resamples = mldata_folds, grid = 10)

######################################################################### Explore xgboost Tuning Results ----

# Visualize tuned parameters
autoplot(xgboost_tune)

final_xgboost <- xgboost_workflow %>% 
  finalize_workflow(select_best(xgboost_tune, "roc_auc")) 
final_xgboost
```
<br>

***

# RANDOM FOREST
```{r os rand_forest}
############################################################################################### Random FOREST ----
set.seed(789)
# Model specification
ranger_spec <- rand_forest(
  # tune right value for the number of predictors that will be randomly sampled at each split when creating the tree models
  mtry = tune(), 
  # tune right value for the minimum number of data points in a node that are required for the node to be split further.
  min_n = tune(),
  trees = 1000) %>% 
  set_mode("classification") %>% 
  set_engine("ranger")

# Set up a work flow
ranger_workflow <- 
  workflow() %>% 
  # Add preprocessor
  add_recipe(mldata_recipe) %>% # here is an unfit mode
  add_model(ranger_spec) # add our model specification

# Tuning
doParallel::registerDoParallel()
set.seed(789)
# will tune mtry and min_m on a grid
ranger_tune <-
  tune_grid(ranger_workflow, # Will take our workflow and apply it on
            resamples = mldata_folds, # each fold of the data for 
            grid = 20) # How many candidate point do I want to try

############################################################################### II ### Explore Tuning Results ----

# Visualize tuned parameters
autoplot(ranger_tune)

final_rf <- ranger_workflow %>% 
  finalize_workflow(select_best(ranger_tune, "accuracy"))
final_rf
```
<br>

***

# LOGISTIC REGRESSION
```{r os logistic_reg}

set.seed(789)

glmnet_spec <- 
  logistic_reg(penalty = tune(), mixture = tune()) %>% # Looks ridge would increase really slightly mixture = 0
  set_mode("classification") %>% 
  set_engine("glmnet") 

glmnet_workflow <- 
  workflow() %>% 
  add_recipe(mldata_recipe) %>% 
  add_model(glmnet_spec) 

glmnet_grid <- tidyr::crossing(penalty = 10^seq(-6, -1, length.out = 20), mixture = c(0, 0.05, 
                                                                                      0.2, 0.4, 0.6, 0.8, 1)) 
set.seed(789)
glmnet_tune <- 
  tune_grid(glmnet_workflow, resamples = mldata_folds, grid = glmnet_grid) 

# Visualize tuned parameters
autoplot(glmnet_tune)

final_glmnet <- glmnet_workflow %>% 
  finalize_workflow(select_best(glmnet_tune, "accuracy")) 
final_glmnet
```
<br>

***

# KKNN

```{r}
kknn_spec <- 
  nearest_neighbor(neighbors = tune(), weight_func = tune()) %>% 
  set_mode("classification") %>% 
  set_engine("kknn") 

kknn_workflow <- 
  workflow() %>% 
  add_recipe(mldata_recipe) %>% 
  add_model(kknn_spec) 

set.seed(789)
kknn_tune <-
  tune_grid(kknn_workflow, 
            resamples = mldata_folds, 
            grid = 20)

autoplot(kknn_tune)

final_kknn <- kknn_workflow %>% 
  finalize_workflow(select_best(kknn_tune, "roc_auc"))
final_kknn
```


```{r os Performance Metrics}
################################################################### Calculate Performance Metrics with tuned model----
set.seed(789)
tree_results <- final_tree %>% 
  fit_resamples(
    resamples = mldata_folds,
    metrics = metric_set(roc_auc, accuracy, sensitivity, specificity),
    control = control_resamples(save_pred = TRUE)
  )

set.seed(789)
xgboost_results <- final_xgboost %>% 
  fit_resamples(
    resamples = mldata_folds,
    metrics = metric_set(roc_auc, accuracy, sensitivity, specificity),
    control = control_resamples(save_pred = TRUE)
  )

set.seed(789)
rf_results <- final_rf %>% 
  fit_resamples( # is not doing any tuning, measuring performance on cross validation data
    resamples = mldata_folds,
    metrics = metric_set(roc_auc, accuracy, sensitivity, specificity),
    control = control_resamples(save_pred = TRUE, verbose = TRUE)
  )

set.seed(789)
glmnet_results <- final_glmnet %>% 
  fit_resamples(
    resamples = mldata_folds,
    metrics = metric_set(roc_auc, accuracy, sensitivity, specificity),
    control = control_resamples(save_pred = TRUE)
  )

set.seed(789)
kknn_results <- final_kknn %>% 
  fit_resamples(
    resamples = mldata_folds,
    metrics = metric_set(roc_auc, accuracy, sensitivity, specificity),
    control = control_resamples(save_pred = TRUE)
  )

###############################################################################  Support vector machine # not necessary
###############################################################################  neural network
```
<br>

***

# Evaluate models
```{r os evaluate models}
rf_results %>% # Compare both models
  collect_predictions() %>% 
  mutate(model = "rf") %>% 
  bind_rows(glmnet_results %>% 
              collect_predictions() %>% 
              mutate(model = "glmet")) %>% 
  bind_rows(xgboost_results %>% 
              collect_predictions() %>% 
              mutate(model = "xgboost")) %>% 
  bind_rows(tree_results %>% 
              collect_predictions() %>% 
              mutate(model = "tree")) %>% 
  bind_rows(kknn_results %>% 
              collect_predictions() %>% 
              mutate(model = "kknn")) %>% 
  group_by(model) %>% 
  roc_curve(vital_new, .pred_Alive) %>% 
  autoplot()

rf_results %>% # Compare both models
  collect_metrics() %>% 
  select(".metric", rf_mean = mean) %>% 
  full_join(., glmnet_results %>% 
              collect_metrics() %>% 
              select(".metric", glmet_mean = mean)
            , by = ".metric") %>% 
  full_join(., xgboost_results %>% 
              collect_metrics() %>% 
              select(".metric", xgboost_mean = mean)
            , by = ".metric") %>% 
  full_join(., tree_results %>% 
              collect_metrics() %>% 
              select(".metric", tree_mean = mean)
            , by = ".metric") %>% 
  full_join(., kknn_results %>% 
              collect_metrics() %>% 
              select(".metric", kknn_mean = mean)
            , by = ".metric")

rf_results %>% # Compare both models
  collect_metrics() %>% 
  mutate(model = "rf") %>% 
  bind_rows(glmnet_results %>% 
              collect_metrics() %>% 
              mutate(model = "glmet")) %>% 
  bind_rows(xgboost_results %>% 
              collect_metrics() %>% 
              mutate(model = "xgboost")) %>% 
  bind_rows(tree_results %>% 
              collect_metrics() %>% 
              mutate(model = "tree")) %>% 
  bind_rows(kknn_results %>% 
              collect_metrics() %>% 
              mutate(model = "kknn")) %>% 
  
  ggplot(aes(x= .metric, y=mean, fill = model))+
  geom_bar(stat = "identity",
           position = position_dodge())+
  geom_errorbar(aes(x = .metric,
                    ymin = mean - std_err,
                    ymax = mean + std_err),
                width = 0.2, alpha = 0.5,
                position=position_dodge(width=0.9))+
  theme_minimal()+
  scale_fill_viridis_d(option = "A")
```

**Random forest and logistic regression are investigated deeper due to their respectivive higher accuracy and specificity results**

```{r os evaluate models2}
rf_results %>% 
  conf_mat_resampled()
glmnet_results %>% 
  conf_mat_resampled()

# Visualization
rf_results %>% 
  collect_predictions() %>% 
  conf_mat(truth = vital_new, estimate = .pred_class) %>% 
  autoplot()+
  ggtitle("Random forest")
glmnet_results %>% 
  collect_predictions() %>% 
  conf_mat(truth = vital_new, estimate = .pred_class) %>% 
  autoplot()+
  ggtitle("logistic regression")
```
<br>

***

# Features importance
```{r os vip}
set.seed(789)

###################################### Ranger
# Need to train the model one more time but without tuning to go faster
set.seed(789)
importance_spec <- ranger_spec %>% 
  finalize_model(select_best(ranger_tune, "roc_auc")) %>% 
  set_engine("ranger", importance = "permutation") # permutation based importance

# represents the mean decrease in node impurity (and not the mean decrease in accuracy)
workflow() %>% 
  add_recipe(mldata_recipe) %>% 
  add_model(importance_spec) %>% 
  fit(train_data) %>% 
  extract_fit_parsnip() %>% 
  vip(aesthetics = list(alpha = 0.5, fill = "midnightblue"),
      # geom = "point",
      num_features = 20
  ) +
  theme_minimal() + 
  ggtitle("Varaiable importance from Random forest model")

###################################### glmnet
# Need to train the model one more time but without tuning to go faster
importance_spec <- glmnet_spec %>% 
  finalize_model(select_best(glmnet_tune, "roc_auc")) %>% 
  set_engine("glmnet", importance = "permutation") # permutation based importance

# represents the mean decrease in node impurity (and not the mean decrease in accuracy)
workflow() %>% 
  add_recipe(mldata_recipe) %>% 
  add_model(importance_spec) %>% 
  fit(train_data) %>% 
  extract_fit_parsnip() %>% 
  vip(aesthetics = list(alpha = 0.5, fill = "midnightblue"),
      # geom = "point",
      num_features = 20
  ) +
  theme_minimal() +
  ggtitle("Varaiable importance from logistic regression model")
```
<br>

***

# Evaluate on the testing dataset
## Fit on testing using tree
### Compare testing performance vs training performance

```{r os fit on testing}
############################################################################################### AT LAST
# Step finalize Fit : fitting to the whole training and evaluating on the testing data
# With the model of our choice
set.seed(789)
final_fit <- final_rf %>% 
  last_fit(data_split)

# Step Explore the modelon testing set
# Collect metrics and compare number with the metrics from the training
# Can see if lower or higher...overfit our data, etc
collect_metrics(final_fit)
# Compare to the training previous number
collect_metrics(rf_results) # as a meminder of previous results
# Test data is a littke lower with samll SD

collect_metrics(final_fit) %>% 
  mutate(set = "testing") %>% 
  rename(mean = .estimate) %>% 
  bind_rows(collect_metrics(rf_results) %>% 
              mutate(set = "training")) %>% 
  filter(str_detect(.metric, "accuracy|roc_auc")) %>% 
  ggplot(aes(x= .metric, y=mean, fill = set))+
  geom_bar(stat = "identity",
           position = position_dodge()) + 
  geom_errorbar(aes(x = .metric,
                    ymin = mean - std_err,
                    ymax = mean + std_err),
                width = 0.2, alpha = 0.5,
                position=position_dodge(width=0.9)) +
  theme_minimal()

```

### Predictions on testing set
```{r os fit on testing2}
final_fit %>% 
  collect_predictions() %>% 
  conf_mat(truth = vital_new, estimate = .pred_class)
final_fit %>% 
  collect_predictions() %>% 
  conf_mat(truth = vital_new, estimate = .pred_class) %>% 
  autoplot() +
  ggtitle("random forest model on testing data")
```

## Fit on testing using GLMET
```{r}
# If choose glmnet, can see estimate on the testing
set.seed(789)
final_fit_sec <- final_glmnet %>% 
  last_fit(data_split)

collect_metrics(final_fit)
# Compare to the training previous number
collect_metrics(glmnet_results)

collect_metrics(final_fit) %>% 
  mutate(set = "testing") %>% 
  rename(mean = .estimate) %>% 
  bind_rows(collect_metrics(glmnet_results) %>% 
              mutate(set = "training")) %>% 
  filter(str_detect(.metric, "accuracy|roc_auc")) %>% 
  ggplot(aes(x= .metric, y=mean, fill = set))+
  geom_bar(stat = "identity",
           position = position_dodge()) + 
  geom_errorbar(aes(x = .metric,
                    ymin = mean - std_err,
                    ymax = mean + std_err),
                width = 0.2, alpha = 0.5,
                position=position_dodge(width=0.9)) +
  theme_minimal()
```


```{r}
final_fit_sec %>%
  pull(.workflow) %>% 
  pluck(1) %>% 
  tidy(exponentiate = TRUE) %>% 
  arrange(desc(abs(estimate))) %>%
  filter(abs(estimate) >0)
# kableExtra::kable(digits = 3)

final_fit_sec %>% # WARNING it uses the scaled data
  pull(.workflow) %>% 
  pluck(1) %>% 
  tidy() %>% 
  filter(term != "(Intercept)") %>% 
  arrange(desc(abs(estimate))) %>% 
  filter(abs(estimate) >0) %>% 
  ggplot(aes(estimate, fct_reorder(term, desc(estimate)), color = estimate > 0))+
  geom_vline(xintercept = 0, color = "lightgrey", lty = 2, size = 1.2) +
  geom_point() + 
  scale_color_discrete(name = "Feature Effect \non outcome", labels = c("Deleterious", "Beneficial")) +
  theme_minimal()+
  ggtitle("Meaningful Parameter Estimate Coefficients using logistic regression model")
```

### Compare both

```{r}
final_fit_sec %>% collect_predictions() %>% 
  mutate(set = "glmnet") %>% 
  bind_rows(final_fit %>% collect_predictions() %>% 
              mutate(set = "rf")) %>% 
  group_by(set) %>% 
  summarize(recurrence = mean(.pred_Dead),
            no_recurrence = mean(`.pred_Alive`)) %>% 
  ungroup() %>% 
  pivot_longer(cols = -set, names_to = "status", values_to = "probability") %>% 
  ggplot(aes(x= set, y=probability, fill = status))+
  geom_bar(stat = "identity",
           position = position_dodge()) +
  theme_minimal()
```
<br>
<br>

***

# Outcome Analysis

<!-- # logistic regression -->
```{r}
os_data <- mldata %>% 
  left_join(., clinical_ml %>% select(mrn, os_event, os_time))
```

## HR
```{r}
tbl1 <- os_data %>% select(os_event, os_time,
                            raceeth, age_at_diagnosis, year_of_diagnosis, tnm_cs_mixed_group_stage, treatment_type,
                            f127avg_3d_rln_, f85com_z_mm, f19statistical_) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = os_data$os_time,
                             event = os_data$os_event)),
                   exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()

tbl2 <- 
  coxph(Surv(time = os_data$os_time,
             event = os_data$os_event) ~ raceeth + age_at_diagnosis + year_of_diagnosis + tnm_cs_mixed_group_stage + treatment_type + f127avg_3d_rln_ + f85com_z_mm + f19statistical_, data =  os_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)

tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```


# Force a split for treatment type

```{r}
# force_fit <- rpart(vital_new ~ . -(treatment_type), data = train_data, maxdepth = 1)
# 
# train_data <- train_data %>% mutate(treatment_type = factor(treatment_type))
# 
# library("partykit")
# tr1 <- ctree(vital_new ~ treatment_type,     data = train_data, maxdepth = 1)
# tr2 <- ctree(vital_new ~ treatment_type + ., data = train_data,
#   subset = predict(tr1, type = "node") == 2)
# tr3 <- ctree(vital_new ~ treatment_type + ., data = train_data,
#   subset = predict(tr1, type = "node") == 3)
# 
# fit2party <- as.party(fit2)
# dataset1 <- data_party(fit2party, id = 2)
# dataset2 <- data_party(fit2party, id = 3)

train_surg <- train_data %>% filter(treatment_type == "Upfront Surgery")
train_neo <- train_data %>% filter(treatment_type == "Upfront Neoadjuvant")

cart_spec <-
   decision_tree(
  #    cost_complexity = 1e-10,
  # tree_depth = 10,
  # min_n = 40
   ) %>%
   set_engine("rpart") %>%
   set_mode("classification")
```

# Upfront surgery
```{r}
set.seed(789)
cart_fit <-
   cart_spec %>%
   fit(vital_new ~ .-mrn , data = train_surg)
cart_fit %>%
  extract_fit_engine() %>%
  rpart.plot()
```

# Upfront neo
```{r}
set.seed(789)
cart_fit <-
   cart_spec %>%
   fit(vital_new ~ .-mrn , data = train_neo)
cart_fit %>%
  extract_fit_engine() %>%
  rpart.plot()




# cart_fit <- repair_call(cart_fit, data = train_data)

# fancyRpartPlot(cart_fit$fit)

# tree_grid <- grid_regular(cost_complexity(),
#                           tree_depth(),
#                           min_n(), levels = 4)
# 
# doParallel::registerDoParallel()
# set.seed(789)
# tree_tune <- tree_workflow %>% 
#   tune_grid(
#     resamples = mldata_folds,
#     grid = tree_grid,
#     metrics = metric_set(roc_auc, accuracy, sensitivity, specificity)
#   )
# # Explore tuning
# autoplot(tree_tune) + theme_light()
# 
# 
# final_tree <- tree_workflow %>% 
#   finalize_workflow(select_best(tree_tune, "roc_auc")) # roc gas a nice curve
# final_tree
# 
# set.seed(789)
# 
# tree_final_fit <- fit(final_tree, data = train_data)
# tree_final_fit
# 
# tree_final_fit %>%
#   extract_fit_engine() %>%
#   rpart.plot()
```









