---
title: "modeling os"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">
.figure {
   margin-top: 25px;
   margin-bottom: 10px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r os setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      # fig.width = 7, fig.height = 5, 
                      fig.align='center'#, fig.show='hold'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

<style>
div.blue { background-color:#FF9966; border-radius: 5px; padding: 20px; font-size: 38px}
</style>
<div class = "blue">

<span style="color: white;">Vital status prediction</span>

</div>
<br>

```{r os library}
library(tidyverse)
library(tidymodels)
# library(broom.mixed) # for converting bayesian models to tidy tibbles
# library(dotwhisker)  # for visualizing regression results
library(themis)
library(gtsummary)
library(ggcorrplot)
library(survival)
```


```{r os load}
clinical <- read_rds("/Users/colinccm/Documents/GitHub/Peres/MilesForMoffittRadiomics/clinical.rds") %>% 
  select(mrn, 
         has_the_patient_recurred, vital_new,
         rec_event, recurrence_time, os_event, os_time,
         age_at_diagnosis, tnm_cs_mixed_group_stage, 
         treatment_type, debulking_status,
         raceeth)

concordance <- read_rds("/Users/colinccm/Documents/GitHub/Peres/MilesForMoffittRadiomics/concordance.rds") %>% 
  filter(value_CCC >= 0.95) %>% 
  select(name) %>% 
  mutate(stable_features = str_match(name, "([a-z][:digit:]*)_*")[,2])

stable_features <- paste0(paste(#"nor_", 
                                concordance$stable_features, "[a-z]", sep = ""), collapse = "|")

mldata <- read_rds("/Users/colinccm/Documents/GitHub/Peres/MilesForMoffittRadiomics/radiomics.rds") %>% 
  select(mrn, contrastenhancementyn, matches(stable_features)) %>% 
  right_join(., clinical %>% 
  select(mrn, vital_new),
             by = "mrn") %>% 
  filter(!is.na(.[2])) %>% 
  mutate(vital_new = factor(vital_new))

clinical <- clinical %>% 
  filter(str_detect(mrn, paste(mldata$mrn, collapse = "|")))
```

# `r emo::ji("question_mark")`

The patient ....... has 2 “biggest” tumor `r emo::ji("check")`  
1 patient has NA in contrast/no contrast variable `r emo::ji("check")`  


# `r emo::ji("memo")` Cohort

From 451 clinical info,  
 - 4 were removed for being grade_differentiation == "Well Differentiated"  
 - 23 were removed for being treatment_type == "Chemo Only" ; **`r emo::ji("question_mark")` Should we include when clinical is not included in our model?**  
 - 26 were removed for being treatment_type == "Surgery Only" (2 overlap with Well Differentiated)  
From 538 radiomics tumor info,  
 - 385 are biggest tumor
 - 344 patients are common with clinical data (aka -19 chemo only, -20 surg only, -3 well diff ; 1 is surg+well diff)  

**We have now 344 patients in our cohort.**


# Data exploration
## Stydy population

<br>

<div class = "row">
<div class = "col-md-5">
```{r}
mldata %>% 
  select(vital_new) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))
```
</div>

<div class = "col-md-7">
```{r}
mldata %>% 
  ggplot(aes(x= vital_new)) + 
  geom_bar(fill = "darkslategray")+
  coord_flip()+
  theme_minimal(base_size = 20)+
  labs(x = NULL)+
  ggtitle("Imbalanced data for recurrence outcome")
```
</div>
</div>

<br>
<br>

# Impact of features on HR

## Features by outcome status
```{r}
rec_data <- mldata %>% 
  left_join(., clinical %>% 
  select(mrn, os_event, os_time), 
  by = "mrn")

rec_data %>% select(matches("^f[0-9]"), vital_new) %>% 
  tbl_summary(by = vital_new, 
              sort = list(everything() ~ "frequency"),
              digits = list(everything() ~  2)) %>% 
  bold_labels() %>% add_p() %>% bold_p(t = .05)
```

## HR of death
```{r}
rec_data <- mldata %>%
  left_join(., clinical %>%
  select(mrn, os_event, os_time),
  by = "mrn")

# rec_data %>% select(matches("^f[0-9]"), os_event, os_time) %>%
#   select(1:20, os_event, os_time) %>%
#   tbl_uvregression(method = survival::coxph,
#                    y = (Surv(time = rec_data$os_time,
#                              event = rec_data$os_event)),
#                    exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
#   bold_labels() %>% italicize_levels()
# 
# rec_data %>% select(matches("^f[0-9]"), os_event, os_time) %>%
#   select(21:40, os_event, os_time) %>%
#   tbl_uvregression(method = survival::coxph,
#                    y = (Surv(time = rec_data$os_time,
#                              event = rec_data$os_event)),
#                    exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
#   bold_labels() %>% italicize_levels()
# rec_data %>% select(matches("^f[0-9]"), os_event, os_time) %>%
#   select(41:60, os_event, os_time) %>%
#   tbl_uvregression(method = survival::coxph,
#                    y = (Surv(time = rec_data$os_time,
#                              event = rec_data$os_event)),
#                    exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
#   bold_labels() %>% italicize_levels()
# rec_data %>% select(matches("^f[0-9]"), os_event, os_time) %>%
#   select(60:ncol(.)) %>%
#   tbl_uvregression(method = survival::coxph,
#                    y = (Surv(time = rec_data$os_time,
#                              event = rec_data$os_event)),
#                    exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
#   bold_labels() %>% italicize_levels()
```


# Build a model
## Splitting the data

The data is split in 3/4 for training and testing for better robustness.  
A strata is applied to the split function to balance contrastenhancementyn in both sets.  
```{r}
# Explore what will need to be changed
skimr::skim(mldata)

set.seed(123)

# 1. Splitting the data
# 3/4 of the data into the training set but split evenly winthin race
data_split <- initial_split(mldata, prop = 3/4, strata = contrastenhancementyn)
# Create training and testing datasets:
train_data <- training(data_split)
test_data  <- testing(data_split)
```

```{r os demo split}
train_data %>% 
  mutate(set = "training") %>% 
  bind_rows(., test_data %>% 
  mutate(set = "testing")) %>% 
  select(vital_new, contrastenhancementyn, set) %>% 
  tbl_summary(by = set,
              type = list(contrastenhancementyn ~ "categorical")) %>% 
  add_p()
```



## Build a recipe

```{r}
# 2. Data pre processing and features engineering + imputation
# Recipe
mldata_recipe <-
  # 1.model formula
  recipe(vital_new ~ ., data = train_data)  %>% 
  # 2.keep these variables but not use them as either outcomes or predictors
  update_role(mrn, new_role = "ID") %>%
  update_role(contrastenhancementyn, new_role = "strata") %>% 

  step_zv(all_predictors()) %>% # or step_nzv
  step_novel(all_nominal(), -all_outcomes()) %>% # Create a previously unseen factor level to a new value.

  # 4.Imputation
  step_unknown(all_nominal_predictors()) %>% 

  step_dummy(all_nominal_predictors()) %>%

  step_smote(vital_new) # Use nearest neighbor to create new synthetic observation almost similar

############################################################################### II ### Data Tuning ----
# train hyperparameter
set.seed(456)
# 10 fold cross validation
mldata_folds <- vfold_cv(train_data, strata = contrastenhancementyn)
```

# DECISION TREE
```{r os decision_tree}
set.seed(789)

# With workflow
tree_spec <- decision_tree(
  cost_complexity = tune(),
  tree_depth = tune(),
  min_n = tune()) %>% 
  set_engine("rpart") %>% 
  set_mode("classification")

tree_workflow <- 
  workflow() %>% 
  add_recipe(mldata_recipe) %>% 
  add_model(tree_spec) 

tree_grid <- grid_regular(cost_complexity(),
                          tree_depth(),
                          min_n(), levels = 4)

doParallel::registerDoParallel()
set.seed(789)
tree_tune <- tree_workflow %>% 
  tune_grid(
    resamples = mldata_folds,
    grid = tree_grid,
    metrics = metric_set(roc_auc, accuracy, sensitivity, specificity)
  )
# Explore tuning
autoplot(tree_tune) + theme_light()

cart_spec <-
   decision_tree(
  #    cost_complexity = 1e-10,
  # tree_depth = 10,
  # min_n = 40
   ) %>%
   set_engine("rpart") %>%
   set_mode("classification")

set.seed(789)
cart_fit <- 
   cart_spec %>%
   fit(vital_new ~ .-mrn-contrastenhancementyn, data = train_data)
cart_fit <- repair_call(cart_fit, data = train_data)

final_tree <- tree_workflow %>% 
  finalize_workflow(select_best(tree_tune, "roc_auc"))
final_tree

tree_final_fit <- fit(final_tree, data = train_data)
tree_final_fit
```


```{r os plot decision_tree, fig.width=12}
library(rpart.plot)
tree_final_fit %>%
  extract_fit_engine() %>%
  rpart.plot()

library(rattle)
fancyRpartPlot(cart_fit$fit)
```


# XGBOOST
```{r os xgboost}
############################################################################################### xgboost----
library(xgboost)
xgboost_spec <- 
  boost_tree(trees = tune(), min_n = tune(), tree_depth = tune(), learn_rate = tune(), 
             loss_reduction = tune(), sample_size = tune()) %>% 
  set_mode("classification") %>% 
  set_engine("xgboost") 

xgboost_workflow <- 
  workflow() %>% 
  add_recipe(mldata_recipe) %>% 
  add_model(xgboost_spec) 

set.seed(789)
xgboost_tune <-
  tune_grid(xgboost_workflow, resamples = mldata_folds, grid = 10)

######################################################################### Explore xgboost Tuning Results ----

# Visualize tuned parameters
autoplot(xgboost_tune)

final_xgboost <- xgboost_workflow %>% 
  finalize_workflow(select_best(xgboost_tune, "roc_auc")) 
final_xgboost
```

# RANDOM FOREST
```{r os rand_forest}
############################################################################################### Random FOREST ----
set.seed(789)
# Model specification
ranger_spec <- rand_forest(
  # tune right value for the number of predictors that will be randomly sampled at each split when creating the tree models
  mtry = tune(), 
  # tune right value for the minimum number of data points in a node that are required for the node to be split further.
  min_n = tune(),
  trees = 1000) %>% 
  set_mode("classification") %>% 
  set_engine("ranger")

# Set up a work flow
ranger_workflow <- 
  workflow() %>% 
  # Add preprocessor
  add_recipe(mldata_recipe) %>% # here is an unfit mode
  add_model(ranger_spec) # add our model specification

# Tuning
doParallel::registerDoParallel()
set.seed(789)
# will tune mtry and min_m on a grid
ranger_tune <-
  tune_grid(ranger_workflow, # Will take our workflow and apply it on
            resamples = mldata_folds, # each fold of the data for 
            grid = 20) # How many candidate point do I want to try

############################################################################### II ### Explore Tuning Results ----

# Visualize tuned parameters
autoplot(ranger_tune)

final_rf <- ranger_workflow %>% 
  finalize_workflow(select_best(ranger_tune, "accuracy"))
final_rf
```

# LOGISTIC REGRESSION
```{r os logistic_reg}

set.seed(789)

glmnet_spec <- 
  logistic_reg(penalty = tune(), mixture = tune()) %>% # Looks ridge would increase really slightly mixture = 0
  set_mode("classification") %>% 
  set_engine("glmnet") 

glmnet_workflow <- 
  workflow() %>% 
  add_recipe(mldata_recipe) %>% 
  add_model(glmnet_spec) 

glmnet_grid <- tidyr::crossing(penalty = 10^seq(-6, -1, length.out = 20), mixture = c(0, 0.05, 
                                                                                      0.2, 0.4, 0.6, 0.8, 1)) 
set.seed(789)
glmnet_tune <- 
  tune_grid(glmnet_workflow, resamples = mldata_folds, grid = glmnet_grid) 

# glmnet_tune <- tune_grid(glmnet_workflow, 
#             resamples = mldata_folds, 
#             grid = 20)
############################################################################### II ### Explore Tuning Results ----


# Visualize tuned parameters
autoplot(glmnet_tune)

final_glmnet <- glmnet_workflow %>% 
  finalize_workflow(select_best(glmnet_tune, "roc_auc")) 
final_glmnet
```

# KKNN

```{r}
kknn_spec <- 
  nearest_neighbor(neighbors = tune(), weight_func = tune()) %>% 
  set_mode("classification") %>% 
  set_engine("kknn") 

kknn_workflow <- 
  workflow() %>% 
  add_recipe(mldata_recipe) %>% 
  add_model(kknn_spec) 

library(kknn)
set.seed(789)
kknn_tune <-
  tune_grid(kknn_workflow, 
            resamples = mldata_folds, 20)

autoplot(kknn_tune)

final_kknn <- kknn_workflow %>% 
  finalize_workflow(select_best(kknn_tune, "roc_auc"))
final_kknn
```


```{r os Performance Metrics}
################################################################### Calculate Performance Metrics with tuned model----
set.seed(789)

tree_results <- final_tree %>% 
  fit_resamples(
    resamples = mldata_folds,
    metrics = metric_set(roc_auc, accuracy, sensitivity, specificity),
    control = control_resamples(save_pred = TRUE)
  )

xgboost_results <- final_xgboost %>% 
  fit_resamples(
    resamples = mldata_folds,
    metrics = metric_set(roc_auc, accuracy, sensitivity, specificity),
    control = control_resamples(save_pred = TRUE)
  )

rf_results <- final_rf %>% 
  fit_resamples( # is not doing any tuning, measuring performance on cross validation data
    resamples = mldata_folds,
    metrics = metric_set(roc_auc, accuracy, sensitivity, specificity),
    control = control_resamples(save_pred = TRUE, verbose = TRUE)
  )

glmnet_results <- final_glmnet %>% 
  fit_resamples(
    resamples = mldata_folds,
    metrics = metric_set(roc_auc, accuracy, sensitivity, specificity),
    control = control_resamples(save_pred = TRUE)
  )

kknn_results <- final_kknn %>% 
  fit_resamples(
    resamples = mldata_folds,
    metrics = metric_set(roc_auc, accuracy, sensitivity, specificity),
    control = control_resamples(save_pred = TRUE)
  )

###############################################################################  Support vector machine # not necessary
###############################################################################  neural network
```

# EVALUATE MODELS
```{r os evaluate models}
rf_results %>% # Compare both models
  collect_predictions() %>% 
  mutate(model = "rf") %>% 
  bind_rows(glmnet_results %>% 
              collect_predictions() %>% 
              mutate(model = "glmet")) %>% 
  bind_rows(xgboost_results %>% 
              collect_predictions() %>% 
              mutate(model = "xgboost")) %>% 
  bind_rows(tree_results %>% 
              collect_predictions() %>% 
              mutate(model = "tree")) %>% 
  bind_rows(kknn_results %>% 
              collect_predictions() %>% 
              mutate(model = "kknn")) %>% 
  group_by(model) %>% 
  roc_curve(vital_new, .pred_Dead) %>% 
  autoplot()

rf_results %>% # Compare both models
  collect_metrics() %>% 
  select(".metric", rf_mean = mean) %>% 
  full_join(., glmnet_results %>% 
              collect_metrics() %>% 
              select(".metric", glmet_mean = mean)
            , by = ".metric") %>% 
  full_join(., xgboost_results %>% 
              collect_metrics() %>% 
              select(".metric", xgboost_mean = mean)
            , by = ".metric") %>% 
  full_join(., tree_results %>% 
              collect_metrics() %>% 
              select(".metric", tree_mean = mean)
            , by = ".metric") %>% 
  full_join(., kknn_results %>% 
              collect_metrics() %>% 
              select(".metric", kknn_mean = mean)
            , by = ".metric")

rf_results %>% # Compare both models
  collect_metrics() %>% 
  mutate(model = "rf") %>% 
  bind_rows(glmnet_results %>% 
              collect_metrics() %>% 
              mutate(model = "glmet")) %>% 
  bind_rows(xgboost_results %>% 
              collect_metrics() %>% 
              mutate(model = "xgboost")) %>% 
  bind_rows(tree_results %>% 
              collect_metrics() %>% 
              mutate(model = "tree")) %>% 
  bind_rows(kknn_results %>% 
              collect_metrics() %>% 
              mutate(model = "kknn")) %>% 
  
  ggplot(aes(x= .metric, y=mean, fill = model))+
  geom_bar(stat = "identity",
           position = position_dodge())+
  geom_errorbar(aes(x = .metric,
                    ymin = mean - std_err,
                    ymax = mean + std_err),
                width = 0.2, alpha = 0.5,
                position=position_dodge(width=0.9))+
  theme_minimal()+
  scale_fill_viridis_d(option = "A")
```

**Random forest and logistic regression are investigated deeper due to their respectivive higher accuracy and specificity results**

```{r os evaluate models2}
tree_results %>% 
  conf_mat_resampled()
glmnet_results %>% 
  conf_mat_resampled()

# Visualization
tree_results %>% # is the saved predictions
  collect_predictions() %>% 
  conf_mat(truth = vital_new, estimate = .pred_class) %>% 
  autoplot()+
  ggtitle("Decision tree")
glmnet_results %>% 
  collect_predictions() %>% 
  conf_mat(truth = vital_new, estimate = .pred_class) %>% 
  autoplot()+
  ggtitle("logistic regression")
```

# features importance
```{r os vip}
library(vip) 
set.seed(789)

###################################### glmnet----
# Need to train the model one more time but without tuning to go faster
importance_spec <- glmnet_spec %>% 
  finalize_model(select_best(glmnet_tune, "roc_auc")) %>% 
  set_engine("glmnet", importance = "permutation") # permutation based importance

# represents the mean decrease in node impurity (and not the mean decrease in accuracy)
workflow() %>% 
  add_recipe(mldata_recipe) %>% 
  add_model(importance_spec) %>% 
  fit(train_data) %>% 
  extract_fit_parsnip() %>% 
  vip(aesthetics = list(alpha = 0.5, fill = "midnightblue"),
      # geom = "point",
      num_features = 20
  ) +
  theme_minimal() +
  ggtitle("Varaiable importance from logistic regression model")


###################################### tree----
set.seed(789)
# Need to train the model one more time but without tuning to go faster
importance_spec <- tree_spec %>% 
  finalize_model(select_best(tree_tune, "roc_auc")) %>% 
  set_engine("rpart", importance = "permutation") # permutation based importance

# represents the mean decrease in node impurity (and not the mean decrease in accuracy)
# workflow() %>% 
#   add_recipe(mldata_recipe) %>% 
#   add_model(importance_spec) %>% 
#   fit(train_data) %>% 
#   extract_fit_parsnip() %>% 
#   vip(aesthetics = list(alpha = 0.5, fill = "midnightblue"),
#       # geom = "point",
#       num_features = 20
#   ) +
#   theme_minimal() + 
#   ggtitle("Varaiable importance from Random forest model")
```

# Fit on testing using tree

```{r os fit on testing}
############################################################################################### AT LAST
# Step finalize Fit : fitting to the whole training and evaluating on the testing data
# With the model of our choice
set.seed(789)
final_fit <- final_tree %>% 
  last_fit(data_split)

# Step Explore the model on testing set
# Collect metrics and compare number with the metrics from the training
# Can see if lower or higher...overfit our data, etc
collect_metrics(final_fit)
# Compare to the training previous number
collect_metrics(tree_results) 

collect_metrics(final_fit) %>% 
  mutate(set = "testing") %>% 
  rename(mean = .estimate) %>% 
  bind_rows(collect_metrics(rf_results) %>% 
              mutate(set = "training")) %>% 
  filter(str_detect(.metric, "accuracy|roc_auc")) %>% 
  ggplot(aes(x= .metric, y=mean, fill = set))+
  geom_bar(stat = "identity",
           position = position_dodge()) + 
  geom_errorbar(aes(x = .metric,
                    ymin = mean - std_err,
                    ymax = mean + std_err),
                width = 0.2, alpha = 0.5,
                position=position_dodge(width=0.9)) +
  theme_minimal()

final_fit %>% 
  collect_predictions() %>% 
  conf_mat(truth = vital_new, estimate = .pred_class)
final_fit %>% 
  collect_predictions() %>% 
  conf_mat(truth = vital_new, estimate = .pred_class) %>% 
  autoplot() +
  ggtitle("random forest model on testing data")

```


```{r os plot tree, fig.width=12}
final_fit %>%
  extract_fit_engine() %>%
  rpart.plot()

# library(rattle)
# fancyRpartPlot(final_fit)


```

# Fit on testing using GLMET
```{r}
# If choose glmnet, can see estimate on the testing
set.seed(789)
final_fit_sec <- final_glmnet %>% 
  last_fit(data_split)

collect_metrics(final_fit)
# Compare to the training previous number
collect_metrics(glmnet_results)

collect_metrics(final_fit) %>% 
  mutate(set = "testing") %>% 
  rename(mean = .estimate) %>% 
  bind_rows(collect_metrics(glmnet_results) %>% 
              mutate(set = "training")) %>% 
  filter(str_detect(.metric, "accuracy|roc_auc")) %>% 
  ggplot(aes(x= .metric, y=mean, fill = set))+
  geom_bar(stat = "identity",
           position = position_dodge()) + 
  geom_errorbar(aes(x = .metric,
                    ymin = mean - std_err,
                    ymax = mean + std_err),
                width = 0.2, alpha = 0.5,
                position=position_dodge(width=0.9)) +
  theme_minimal()
```


```{r}
final_fit_sec %>%
  pull(.workflow) %>% 
  pluck(1) %>% 
  tidy(exponentiate = TRUE) %>% 
  arrange(desc(abs(estimate))) %>%
  filter(abs(estimate) >0)
# kableExtra::kable(digits = 3)

final_fit_sec %>% # WARNING it uses the scaled data
  pull(.workflow) %>% 
  pluck(1) %>% 
  tidy() %>% 
  filter(term != "(Intercept)") %>% 
  arrange(desc(abs(estimate))) %>% 
  filter(abs(estimate) >0) %>% 
  ggplot(aes(estimate, fct_reorder(term, desc(estimate)), color = estimate > 0))+
  geom_vline(xintercept = 0, color = "lightgrey", lty = 2, size = 1.2) +
  geom_point() + 
  scale_color_discrete(name = "Feature Effect \non outcome", labels = c("Deleterious", "Beneficial")) +
  theme_minimal()+
  ggtitle("Meaningful Parameter Estimate Coefficients using logistic regression model")
```

## Compare both

```{r}
final_fit_sec %>% collect_predictions() %>% 
  mutate(set = "glmnet") %>% 
  bind_rows(final_fit %>% collect_predictions() %>% 
              mutate(set = "rf")) %>% 
  group_by(set) %>% 
  summarize(recurrence = mean(.pred_Dead),
            no_recurrence = mean(`.pred_Alive`)) %>% 
  ungroup() %>% 
  pivot_longer(cols = -set, names_to = "status", values_to = "probability") %>% 
  ggplot(aes(x= set, y=probability, fill = status))+
  geom_bar(stat = "identity",
           position = position_dodge()) +
  theme_minimal()
```
<br>
<br>

***

# Outcome Analysis

<!-- # logistic regression -->
```{r}
rec_data <- mldata %>%
  inner_join(., clinical %>%
  select(mrn, os_event, os_time,
         treatment_type, age_at_diagnosis, raceeth, tnm_cs_mixed_group_stage, debulking_status),
  by = "mrn")
```

# HR
```{r}
tbl1 <- rec_data %>% select(os_event, os_time,
                            raceeth, age_at_diagnosis, tnm_cs_mixed_group_stage, treatment_type,
                            f10statistical_, f81com_y_pxl, f9statistical_9,
                            f102avgcoocurre, f65flatness, f83com_x_mm, f87weighted_com) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = rec_data$os_time,
                             event = rec_data$os_event)),
                   exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()

tbl2 <- 
  coxph(Surv(time = rec_data$os_time,
             event = rec_data$os_event) ~ raceeth + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + f10statistical_ + f81com_y_pxl + f9statistical_9 + f102avgcoocurre + f65flatness + f83com_x_mm + f87weighted_com, data =  rec_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)

tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```











