---
title: "Radiomics cleaning data report"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: darkly #cerulean
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">
.figure {
   margin-top: 25px;
   <!-- margin-bottom: 100px; -->
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      # fig.width = 7, fig.height = 5, 
                      fig.align='center'#, fig.show='hold'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

```{r library}
library(tidyverse)
# library(scales)
library(lubridate)
library(data.table)
library(gtsummary)
library(gplots)
library(heatmap.plus)
library(RColorBrewer)
library(psych)
# library(corrplot)
library(ggcorrplot)
library(survival)
library(survminer)
```

# Report Radiomics project
<br>
<br>
<!-- Leave a space here -->

***
## I.Radiomics

```{r radiomics}
radiomics <- read_rds(paste0(here::here(), "/radiomics.rds"))
features <- radiomics %>% 
  select(mrn, lesionid, starts_with("nor"))
# class(features) <- "data.frame"
```

We have radiomics data on `r length(unique(features$mrn))` patients.

<br>
<br>
<!-- Leave a space here -->

***
## II.Clinical
<!-- Here a quick look at the clinical data -->
```{r clinical}
# head(clinical)
```
<!-- <br> -->
<!-- <br> -->
<!-- Leave a space here -->

### 1.Demographics
Some cleanup needs to be done here to combined multiple race_cancer_registry, ethnicity_cancer_registry and others. Let me know how you would prefer them!
I re-calculate the age_at_Dx myself to have more digits.
```{r demo}
radiomics %>% mutate(dataset = "Patients") %>% distinct(mrn, .keep_all = TRUE) %>% 
  select(dataset, race_cancer_registry, ethnicity_cancer_registry, primary_site, histology, 
         tnm_cs__mixed_group_stage, vital_new, age_at_diagnosis, age_at_Dx,
         has_the_patient_recurred_, germline_brca1_mutation, germline_brca2_mutation, 
         somatic_brca1_mutation, somatic_brca2_mutation, any__unclassified__brca_mutation) %>% 
  tbl_summary(by = dataset, 
              sort = list(everything() ~ "frequency", tnm_cs__mixed_group_stage ~ "alphanumeric"),
              digits = list(age_at_Dx ~ c(2, 2))) %>% 
  bold_labels()
```
<br>
<br>
<!-- Leave a space here -->

### 2.Treatment
Some variable will need to be combined here like Surg/chem and Surg/horm in summary_of_rx__1st_course variable.

<div class = "row">
<div class = "col-md-6">
```{r treatment}
radiomics %>% mutate(dataset = "Patients") %>% distinct(mrn, .keep_all = TRUE) %>% 
  select(treatment__type, summary_of_rx__1st_course, summary_of_rx__1st_course__at_t, 
         debulking_status,
         months_at_first_neoadjuvant_chem, months_at_first_adjuvant_chem, months_at_first_surgery) %>% 
  tbl_summary(sort = list(everything() ~ "frequency")) %>% add_n() %>% 
  bold_labels()
```
</div>

<div class = "col-md-6">
<br>
```{r treatment22}
radiomics %>% distinct(mrn, .keep_all = TRUE) %>% 
  ggplot(aes(x= treatment__type)) + 
  geom_bar()+
  coord_flip()+
  theme_minimal(base_size = 20)
```


```{r treatment23}
radiomics %>% distinct(mrn, .keep_all = TRUE) %>% 
  ggplot(aes(x= summary_of_rx__1st_course)) + 
  geom_bar()+
  coord_flip()+
  theme_minimal(base_size = 20)
```

<br>
<br>
<br>
<br>
<br>
```{r treatment24}
radiomics %>% distinct(mrn, .keep_all = TRUE) %>% 
  ggplot(aes(x= debulking_status)) + 
  geom_bar()+
  coord_flip()+
  theme_minimal(base_size = 20)
```
</div>
</div>

```{r treatment demo}
radiomics %>% mutate(dataset = "Patients") %>% distinct(mrn, .keep_all = TRUE) %>% 
  select(treatment__type, race_cancer_registry, ethnicity_cancer_registry, 
         primary_site, histology, tnm_cs__mixed_group_stage) %>% 
  tbl_summary(by = treatment__type, 
              sort = list(everything() ~ "frequency", tnm_cs__mixed_group_stage ~ "alphanumeric")) %>% 
  bold_labels() %>% add_p() %>% bold_p(t = .05) %>% add_overall()
```

```{r treatment25}
# Table treatment
radiomics %>% mutate(dataset = "Patients") %>% distinct(mrn, .keep_all = TRUE) %>% 
  select(treatment__type, summary_of_rx__1st_course, debulking_status) %>% 
  tbl_summary(by = treatment__type, 
              sort = list(everything() ~ "frequency")) %>% 
  bold_labels() %>% add_p() %>% bold_p(t = .05) %>% add_overall()
```

<br>
<br>
<!-- Leave a space here -->

### 3.Treatment and outcomes
Here I added a new variable to look at recurrence after surgery

```{r treatment1}
radiomics %>% mutate(dataset = "Patients") %>% distinct(mrn, .keep_all = TRUE) %>% 
  select(treatment__type, "age_at_Dx", vital_new, has_the_patient_recurred_, has_the_patient_recurred_after_surg,
         "months_at_first_neoadjuvant_chem", "months_at_first_surgery", "months_at_first_adjuvant_chem", 
         "months_at_first_chemo", "age_at_surgery",  "age_at_first_recurrence", "month_at_first_recurrence") %>% 
  tbl_summary(by = treatment__type,
              digits = list(everything()~ 2),
              missing = "no") %>% 
  bold_labels() %>% add_n() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```

<br>
<br>
<!-- Leave a space here -->

### 4.Recurrence
```{r recurrence}
# Table treatment by recurrence
radiomics %>% mutate(dataset = "Patients") %>% distinct(mrn, .keep_all = TRUE) %>% 
  select(treatment__type, debulking_status, has_the_patient_recurred_, tnm_cs__mixed_group_stage, summary_of_rx__1st_course) %>% 
  tbl_summary(by = has_the_patient_recurred_, 
              sort = list(everything() ~ "frequency")) %>% 
  bold_labels() %>% add_p() %>% bold_p(t = .05) %>% add_overall()

# radiomics %>% mutate(dataset = "Patients") %>% distinct(mrn, .keep_all = TRUE) %>% 
#   select(treatment__type, has_the_patient_recurred_, has_the_patient_recurred_after_surg) %>% 
#   tbl_summary(by = treatment__type, 
#               sort = list(everything() ~ "frequency")) %>% 
#   bold_labels() %>% add_p() %>% bold_p(t = .05)
```


```{r recurrence1}
# radiomics %>% mutate(dataset = "Patients") %>% distinct(mrn, .keep_all = TRUE) %>% 
#   select(treatment__type, has_the_patient_recurred_after_surg) %>% 
#   tbl_summary(by = treatment__type, 
#               sort = list(everything() ~ "frequency")) %>% 
#   bold_labels() %>% add_p() %>% bold_p(t = .05)


tbl1 <- radiomics %>% mutate(dataset = "Patients") %>% distinct(mrn, .keep_all = TRUE) %>% 
  select(treatment__type, month_at_first_recurrence, months_of_surg_rec_free) %>% 
  tbl_summary(by = treatment__type, 
              digits = list(everything() ~ 2)) %>% 
  bold_labels() %>% add_p() %>% bold_p(t = .05)
tbl2 <- radiomics %>% mutate(dataset = "Patients") %>% distinct(mrn, .keep_all = TRUE) %>% 
  select(debulking_status, month_at_first_recurrence, months_of_surg_rec_free) %>% 
  tbl_summary(by = debulking_status, 
              digits = list(everything() ~ 2)) %>% 
  bold_labels() %>% add_p() %>% bold_p(t = .05)
tbl3 <- radiomics %>% mutate(dataset = "Patients") %>% distinct(mrn, .keep_all = TRUE) %>% 
  select(tnm_cs__mixed_group_stage, month_at_first_recurrence, months_of_surg_rec_free) %>% 
  tbl_summary(by = tnm_cs__mixed_group_stage, 
              digits = list(everything() ~ 2)) %>% 
  bold_labels() %>% add_p() %>% bold_p(t = .05)
tbl4 <- radiomics %>% mutate(dataset = "Patients") %>% distinct(mrn, .keep_all = TRUE) %>% 
  select(summary_of_rx__1st_course, month_at_first_recurrence, months_of_surg_rec_free) %>% 
  tbl_summary(by = summary_of_rx__1st_course, 
              digits = list(everything() ~ 2)) %>% 
  bold_labels() %>% add_p() %>% bold_p(t = .05)

tbl_merge(list(tbl1, tbl2, tbl3, tbl4),
          tab_spanner = c("**treatment__type**", "**debulking_status**", "**tnm_cs__mixed_group_stage**", "**summary_of_rx__1st_course**")) %>%
  bold_labels() %>%
  italicize_levels()
```
<br>
<br>
<!-- Leave a space here -->

### 5.BRCA & Recurrence

```{r brca}
# Plot brca germline somatic
radiomics %>% distinct(mrn, .keep_all = TRUE) %>% 
  select(mrn, germline_brca1_mutation, somatic_brca1_mutation, germline_brca2_mutation, somatic_brca2_mutation) %>% 
  pivot_longer(cols = c(germline_brca1_mutation, somatic_brca1_mutation, germline_brca2_mutation, somatic_brca2_mutation), 
               names_to = "name",values_to = "value") %>%
  filter(value == "Yes") %>% 
  mutate(brca = case_when(
    str_detect(name, "brca1") ~ "brca1",
    str_detect(name, "brca2") ~ "brca2"
  )) %>% 
  mutate(name = str_remove_all(name, "_brca1|_brca2|_mutation")) %>%
  group_by(name, brca) %>% 
  summarise(count=n()) %>%
  ggplot(aes(x = brca, y= count, fill= name)) + 
  geom_bar(stat = "identity")+
  geom_text(aes(label = paste0("n=", count)), size = 3, position = position_stack(vjust = 0.5))+
  theme_minimal()

# Table brca by recurrence
radiomics %>% mutate(dataset = "Patients") %>% distinct(mrn, .keep_all = TRUE) %>% 
  select(has_the_patient_recurred_, germline_brca1_mutation, germline_brca2_mutation, 
         somatic_brca1_mutation, somatic_brca2_mutation, any__unclassified__brca_mutation) %>%
  tbl_summary(by = has_the_patient_recurred_, 
              sort = list(everything() ~ "frequency"),
              missing = "no") %>% 
  bold_labels() %>% add_p() %>% bold_p(t = .05) %>% add_overall()

# Table brca by treatment
radiomics %>% mutate(dataset = "Patients") %>% distinct(mrn, .keep_all = TRUE) %>% 
  select(treatment__type, germline_brca1_mutation, germline_brca2_mutation, 
         somatic_brca1_mutation, somatic_brca2_mutation, any__unclassified__brca_mutation) %>%
  tbl_summary(by = treatment__type, 
              sort = list(everything() ~ "frequency"),
              missing = "no") %>% 
  bold_labels() %>% add_p() %>% bold_p(t = .05) %>% add_overall()
```
<br>
<br>
<!-- Leave a space here -->

### 6.Comorbidities
```{r}
radiomics %>% mutate(dataset = "Patients") %>% distinct(mrn, .keep_all = TRUE) %>% 
  mutate(pre_dx_hypertension = ifelse(str_detect(hypertension, "pre|Pre"), "hypertension", "no hypertension")) %>% 
  mutate(pre_dx_diabetes = ifelse(str_detect(diabetes_mellitus, "pre|Pre"), "diabetes", "no diabetes")) %>% 
  mutate(pre_dx_hypercholesterolemia = ifelse(str_detect(hypercholesterolemia, "pre|Pre"), 
                                              "hypercholesterolemia", "no hypercholesterolemia")) %>% 
  mutate(pre_dx_CKd = ifelse(str_detect(chronic_kidney_disease, "pre|Pre"), "CKd", "no CKd")) %>% 
  mutate(pre_dx_cardiac_conditions = ifelse(str_detect(cardiac_conditions_including_bu, "pre|Pre"), 
                                            "cardiac conditions", "no cardiac conditions")) %>% 
  select("has_the_patient_recurred_", "pre_dx_hypertension", "pre_dx_diabetes",
         "pre_dx_hypercholesterolemia", "pre_dx_CKd", "pre_dx_cardiac_conditions") %>%
  tbl_summary(by = has_the_patient_recurred_, 
              sort = list(everything() ~ "frequency"),
              missing = "no") %>%
  # modify_spanning_header(starts_with("stat_") ~ "**Randomization Assignment**")
  bold_labels() %>% add_p() %>% bold_p(t = .05) %>% add_overall()
  # show_header_names(a)

radiomics %>% mutate(dataset = "Patients") %>% distinct(mrn, .keep_all = TRUE) %>% 
  mutate(pre_dx_hypertension = ifelse(str_detect(hypertension, "pre|Pre"), "hypertension", "no hypertension")) %>% 
  mutate(pre_dx_diabetes = ifelse(str_detect(diabetes_mellitus, "pre|Pre"), "diabetes", "no diabetes")) %>% 
  mutate(pre_dx_hypercholesterolemia = ifelse(str_detect(hypercholesterolemia, "pre|Pre"), 
                                              "hypercholesterolemia", "no hypercholesterolemia")) %>% 
  mutate(pre_dx_CKd = ifelse(str_detect(chronic_kidney_disease, "pre|Pre"), "CKd", "no CKd")) %>% 
  mutate(pre_dx_cardiac_conditions = ifelse(str_detect(cardiac_conditions_including_bu, "pre|Pre"), 
                                            "cardiac conditions", "no cardiac conditions")) %>% 
  select(treatment__type, "pre_dx_hypertension", "pre_dx_diabetes",
         "pre_dx_hypercholesterolemia", "pre_dx_CKd", "pre_dx_cardiac_conditions") %>%
  tbl_summary(by = treatment__type, 
              sort = list(everything() ~ "frequency"),
              missing = "no") %>%
  # modify_spanning_header(starts_with("stat_") ~ "**Randomization Assignment**")
  bold_labels() %>% add_p() %>% bold_p(t = .05) %>% add_overall()
```
<br>
<br>
<!-- Leave a space here -->

***
## III.Survivals
The legend are long and will be adjusted later.

### 1.General
<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 7}
radiomics_surv <- radiomics %>% distinct(mrn, .keep_all = TRUE)
# From Dx
# overall survival by 4 trt groups
ggsurvplot(survfit(Surv(months_at_dx_followup, os_event) ~ treatment__type, data=radiomics_surv),
           title = "Overall survival from date of diagnosis", 
           font.main = c(18, "bold", "black"), 
           font.x = c(16, "bold", "black"), font.y = c(16, "bold", "black"), 
           font.legend = c(12, "bold", "black"), font.tickslab = c(14, "bold", "black"),
           size = 1.5,
           
           pval=TRUE, palette = c("black", "green","blue", "red"),
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (count(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4,tables.height = 0.25,
           tables.theme = theme_survminer(base_size = 8,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(13, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)", ylab="Survival Probability"  
           # # legend.labs=c("chemo only", "surgery only", "upfront neoadjuvant", "upfront surgery")
           ) + guides(colour = guide_legend(nrow = 2))
```
</div>

<div class = "col-md-6">
```{r, fig.height = 7}
# recurrence free survival by 4 trt groups
ggsurvplot(survfit(Surv(months_of_dx_rec_free, rec_event) ~ treatment__type, data=radiomics_surv),
           title = "Recurrence free survival from date of diagnosis", 
           font.main = c(18, "bold", "black"), 
           font.x = c(16, "bold", "black"), font.y = c(16, "bold", "black"), 
           font.legend = c(12, "bold", "black"), font.tickslab = c(14, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (count(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4,tables.height = 0.25,
           tables.theme = theme_survminer(base_size = 8,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(13, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)", ylab="Recurrence Probability"  
           # legend.labs=c("chemo only", "surgery only", "upfront neoadjuvant", "upfront surgery")
           ) + guides(colour = guide_legend(nrow = 2))
```
</div>
</div>

### 2.From surgery
<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 7}
# 
# overall survival calculated from date of upfront surgery 
ggsurvplot(survfit(Surv(months_at_surg_followup, os_event) ~ treatment__type, data=radiomics_surv), 
           title = "Overall survival from date of upfront surgery", 
           font.main = c(18, "bold", "black"), 
           font.x = c(16, "bold", "black"), font.y = c(16, "bold", "black"), 
           font.legend = c(12, "bold", "black"), font.tickslab = c(14, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (count(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4,tables.height = 0.25,
           tables.theme = theme_survminer(base_size = 8,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(13, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)", ylab="Survival Probability"#,  
           # # legend.labs=c("chemo only", "surgery only", "upfront neoadjuvant", "upfront surgery")
           ) + guides(colour = guide_legend(nrow = 2))
```
</div>

<div class = "col-md-6">
```{r, fig.height = 7}
# recurrence free survival calculated from date of upfront surgery 
ggsurvplot(survfit(Surv(months_of_surg_rec_free, rec_event) ~ treatment__type, data=radiomics_surv),
           title = "Recurrence free survival from date of upfront surgery ", 
           font.main = c(18, "bold", "black"), 
           font.x = c(16, "bold", "black"), font.y = c(16, "bold", "black"), 
           font.legend = c(12, "bold", "black"), font.tickslab = c(14, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (count(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4,tables.height = 0.25,
           tables.theme = theme_survminer(base_size = 8,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(13, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)", ylab="Recurrence Probability"#,  
           # # legend.labs=c("chemo only", "surgery only", "upfront neoadjuvant", "upfront surgery")
) + guides(colour = guide_legend(nrow = 2))
```
</div>
</div>

### 3.From neoadjuvant
<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 7}
# 
# overall survival calculated from date of neoadjuvant 
ggsurvplot(survfit(Surv(months_at_neo_followup, os_event) ~ treatment__type, data=radiomics_surv),
           title = "Overall survival from date of neoadjuvant", 
           font.main = c(18, "bold", "black"), 
           font.x = c(16, "bold", "black"), font.y = c(16, "bold", "black"), 
           font.legend = c(12, "bold", "black"), font.tickslab = c(14, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (count(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4,tables.height = 0.25,
           tables.theme = theme_survminer(base_size = 8,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(13, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)", ylab="Survival Probability"#,  
           # # legend.labs=c("chemo only", "surgery only", "upfront neoadjuvant", "upfront surgery")
) + guides(colour = guide_legend(nrow = 2))
```
</div>

<div class = "col-md-6">
```{r, fig.height = 7}
# recurrence free survival calculated from date of neoadjuvant 
ggsurvplot(survfit(Surv(months_of_neo_rec_free, rec_event) ~ treatment__type, data=radiomics_surv),
           title = "Recurrence free survival from date of neoadjuvant", 
           font.main = c(18, "bold", "black"), 
           font.x = c(16, "bold", "black"), font.y = c(16, "bold", "black"), 
           font.legend = c(12, "bold", "black"), font.tickslab = c(14, "bold", "black"),
           size = 1.5,
           
           pval=TRUE, palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (count(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4,tables.height = 0.25,
           tables.theme = theme_survminer(base_size = 8,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(13, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)", ylab="Recurrence Probability"#,  
           # # legend.labs=c("chemo only", "surgery only", "upfront neoadjuvant", "upfront surgery")
) + guides(colour = guide_legend(nrow = 2))
```
</div>
</div>

### 4.From treatment
<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 7}
# 
# overall survival calculated from date of treatment 
ggsurvplot(survfit(Surv(months_at_treat_followup, os_event) ~ treatment__type, data=radiomics_surv),
           title = "Overall survival from date of treatment", 
           font.main = c(18, "bold", "black"), 
           font.x = c(16, "bold", "black"), font.y = c(16, "bold", "black"), 
           font.legend = c(12, "bold", "black"), font.tickslab = c(14, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (count(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4,tables.height = 0.25,
           tables.theme = theme_survminer(base_size = 8,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(13, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)", ylab="Survival Probability"#,  
           # # legend.labs=c("chemo only", "surgery only", "upfront neoadjuvant", "upfront surgery")
) + guides(colour = guide_legend(nrow = 2))
```
</div>

<div class = "col-md-6">
```{r, fig.height = 7}
# recurrence free survival calculated from date of treatment 
ggsurvplot(survfit(Surv(months_of_treat_rec_free, rec_event) ~ treatment__type, data=radiomics_surv),
           title = "Recurrence free survival from date of treatment", 
           font.main = c(18, "bold", "black"), 
           font.x = c(16, "bold", "black"), font.y = c(16, "bold", "black"), 
           font.legend = c(12, "bold", "black"), font.tickslab = c(14, "bold", "black"), 
           size = 1.5,
           
           pval=TRUE, palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (count(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4,tables.height = 0.25,
           tables.theme = theme_survminer(base_size = 8,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(13, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)", ylab="Recurrence Probability"#,  
           # # legend.labs=c("chemo only", "surgery only", "upfront neoadjuvant", "upfront surgery")
) + guides(colour = guide_legend(nrow = 2))
```
</div>
</div>

### 5.In stage3/4 group
<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 7}
restricted_stage_trt_type_ <- radiomics_surv %>% filter(str_detect(tnm_cs__mixed_group_stage, "3|4"))
# overall survival in stage3/4 group of patients by upfront noeadj vs. upfront surgery groups
ggsurvplot(survfit(Surv(months_at_dx_followup, os_event) ~ treatment__type, data=restricted_stage_trt_type_),
           title = "Overall survival from date of diagnosis",
           font.main = c(18, "bold", "black"),
           font.x = c(16, "bold", "black"), font.y = c(16, "bold", "black"),
           font.legend = c(12, "bold", "black"), font.tickslab = c(14, "bold", "black"),
           size = 1.5,
           
           pval=TRUE, palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (count(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4,tables.height = 0.25,
           tables.theme = theme_survminer(base_size = 2,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(13, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)", ylab="Survival Probability"#,  
           # # legend.labs=c("upfront neoadjuvant", "upfront surgery")
           ) + guides(colour = guide_legend(nrow = 2))
```
</div>

<div class = "col-md-6">
```{r, fig.height = 7}
ggsurvplot(survfit(Surv(months_of_dx_rec_free, rec_event) ~ treatment__type, data=restricted_stage_trt_type_),
           title = "Recurrence free survival from date of diagnosis",
           font.main = c(18, "bold", "black"),
           font.x = c(16, "bold", "black"), font.y = c(16, "bold", "black"),
           font.legend = c(12, "bold", "black"), font.tickslab = c(14, "bold", "black"),
           size = 1.5,
           
           pval=TRUE, palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (count(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 4,tables.height = 0.25,
           tables.theme = theme_survminer(base_size = 1,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(13, "bold", "black")
           ),
           
           legend.title = "", xlab = "Time (in months)", ylab="Recurrence Probability"#,  
           # # legend.labs=c("upfront neoadjuvant", "upfront surgery")
           ) + guides(colour = guide_legend(nrow = 2))
```
</div>
</div>

<br>
<br>

***
## IV.Regression
```{r}
model <- glm(recurremce ~ treatment__type + preDx_comorbidities + age_at_Dx + race_cancer_registry + tnm_cs__mixed_group_stage + debulking_status, data = radiomics, family = binomial)
tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
tbl2 <- tbl_regression(model, exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
```

<br>
<br>

&nbsp;
<hr />
<p style="text-align: center;">Code in <a href="https://github.com/PeresLabAtMoffitt/MilesForMoffittRadiomics">PeresLabAtMoffitt </a>GitHub </p>

<!-- ###  -->
<!-- <div class = "row"> -->
<!-- <div class = "col-md-6"> -->
<!-- ```{r} -->

<!-- ``` -->
<!-- </div> -->

<!-- <div class = "col-md-6"> -->
<!-- ```{r} -->

<!-- ``` -->
<!-- </div> -->
<!-- </div> -->