---
title: "Radiomics stable features"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">
.figure {
   margin-top: 25px;
   <!-- margin-bottom: 100px; -->
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      # fig.width = 7, fig.height = 5, 
                      fig.align='center'#, fig.show='hold'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

```{r library}
library(tidyverse)
# library(lubridate)
library(data.table)
# library(gtsummary)
# library(gplots)
# library(heatmap.plus)
library(RColorBrewer)
library(irr)
# library(ggcorrplot)
# library(survival)
# library(survminer)
library(DescTools)
library(plotly)
```

<br>

```{r load test-retest}
path <- fs::path("", "Volumes", "Peres_Research", "Ovarian - Radiomics")

first_seg <- read_csv(paste0(path,
  "/data/Test retest stable features/Ovarian_Radiomics_Features_TestRetest_first segmentation.csv")) %>%
  `colnames<-`(str_remove(colnames(.), " _first_segmentation") %>% tolower() %>% gsub(":", "_",.)) %>% 
  mutate(date = as.Date(date, format = "%m/%d/%y"))

second_seg <- read_csv(paste0(path,
  "/data/Test retest stable features/Ovarian_Radiomics_Features_TestRetest_second segmentation.csv")) %>%
  `colnames<-`(str_remove(colnames(.), " _second_seg") %>% tolower() %>% gsub(":", "_",.)) %>% 
  mutate(date = as.Date(as.character(date), format = "%Y%m%d")) %>% 
  mutate(f133_glszm_small_zone_emphasis = as.numeric(f133_glszm_small_zone_emphasis)) %>% 
  mutate(f138_glszm_small_zone_high_grey_level_emphasis = as.numeric(f138_glszm_small_zone_high_grey_level_emphasis))
  
# Remove image that are not contrast enhanced
ids_to_remove <- read_csv(paste0(path,
  "/data/Test retest stable features/List of ids to remove from test retest.csv"))
ids_to_remove <- paste(ids_to_remove$ids_non_contrast_enhamced, collapse = "|")

segmentation <- bind_rows(first_seg, second_seg) %>% 
  filter(!str_detect(mrn, ids_to_remove)) %>% 
  mutate(seg = "segmentation0") %>% 
  unite(segmentationcohort, c(seg, segmentationcohort), sep = "") %>% 
  mutate(mrn = as.character(mrn)) %>% 
  # select(-c(date, 'lesion id', 'segmented by')) %>% 
  as.data.frame(.)
```

***

<br>

# CCC
The features noted as stable have a CCC >= 0.95.
The following table is saved at   
smb://hlm/data/project/Peres_Research/Ovarian - Radiomics/Christelle/stable features/selected stable features at 95p.csv
```{r CCC, rows.print=75}
CCC_data <- data.frame(matrix(nrow=1, ncol=0)) #data.frame(x = c("variable", "CCC"))
for(i in 1:length(colnames(segmentation))) {
  
  rad <- segmentation %>% select(mrn, segmentationcohort)
  
  if(class(segmentation[,i]) == "numeric" | class(segmentation[,i]) == "integer") {
    
    CCC_df <- cbind(rad, value = segmentation[,i])
    CCC_df <- CCC_df %>%
      pivot_wider(names_from = segmentationcohort, values_from = value) %>%
      select(c(starts_with("segmentation0")))
    
    CCC <- round(CCC(x=CCC_df$segmentation01, y=CCC_df$segmentation02, ci = "z-transform", conf.level = 0.95, na.rm = FALSE)$rho.c$est, 3)
    CCC_data <- cbind(CCC_data,CCC)
    
  }
  
}
colnames(CCC_data) <- colnames(segmentation)[6:ncol(segmentation)]
rm(CCC_df, CCC, i, rad)

plot <- CCC_data %>% 
  pivot_longer(cols = everything()) %>% 
  mutate(CCC = "CCC") %>% 
  mutate(reliability = case_when(
    value < 0.95 ~ "not considred as stable",
    value >= 0.95 ~ "stable"
  )) %>% 
  mutate(text = paste("Feature: ", name, "\nCCC: ", round(value, 2), "\nReliability: ", reliability, sep="")) %>% 
  ggplot(aes(x = CCC, y = value, color = reliability, text=text))+
  labs(title = "Reliability of the radiomic features based on CCC value", x= NULL, y= "CCC value")+
  scale_color_brewer(palette = "Set2") +
  scale_x_discrete(labels = "")+
  theme_minimal()+
  geom_point(size = 1, position=position_jitter(w=0.8))
plot <- ggplotly(plot, tooltip="text")
plot

CCC_data <- CCC_data %>% 
  pivot_longer(cols = everything()) %>% 
  mutate(reliability = case_when(
    value >= 0.95      ~ "stable",
    TRUE               ~ "not considred as stable"
  )) %>% arrange(desc(value))
CCC_data

path <- fs::path("", "Volumes", "Peres_Research", "Ovarian - Radiomics", "Christelle")
# write_csv(CCC_data %>% filter(value > 0.95), paste0(path, "/stable features/selected stable features at 95p.csv"))
```
<br>

# ICC
I first used the ICC for a single rater, wo-way mixed effects model with a measure for absolute agreement (I found that the two-way mixed-effects model and the absolute agreement are recommended for both test-retest and intra-rater reliability studies (Koo et al., 2016) so I wanted to compare with CCC).  
**For ICC, a value of 0.9 is considered as excellent.**  

```{r ICC}
ICC_data <- data.frame(matrix(nrow=1, ncol=0)) #data.frame(x = c("variable", "ICC"))
for(i in 1:length(colnames(segmentation))) {
  
  rad <- segmentation %>% select(mrn, segmentationcohort)
  
  if(class(segmentation[,i]) == "numeric" | class(segmentation[,i]) == "integer") {
    
    ICC_df <- cbind(rad, value = segmentation[,i])
    ICC_df <- ICC_df %>%
      pivot_wider(names_from = segmentationcohort, values_from = value) %>%
      select(c(starts_with("segmentation0")))
    
    # ICC <- ICC(ICC_df)$results[3,2] # 2 way mixed effect for single rater
    ICC <- round(icc(
      ICC_df, model = "twoway", 
      type = "agreement", unit = "single"
    )$value, 3)
    ICC_data <- cbind(ICC_data,ICC)
    
  }
  
}
colnames(ICC_data) <- colnames(segmentation)[6:ncol(segmentation)]
rm(ICC_df, ICC, i, rad)

plot <- ICC_data %>% 
  pivot_longer(cols = everything()) %>% 
  mutate(ICC = "ICC") %>% 
  mutate(reliability = case_when(
    value < 0.5 ~ "poor",
    value >= 0.5 &
      value < 0.75 ~ "moderate",
    value >= 0.75 &
      value < 0.9 ~ "good",
    value >= 0.9 ~ "excellent"
  )) %>% 
  mutate(text = paste("Feature: ", name, "\nICC: ", round(value, 2), "\nReliability: ", reliability, sep="")) %>% 
  ggplot(aes(x = ICC, y = value, color = reliability, text=text))+
  labs(title = "Reliability of the radiomic features based on ICC value", x= NULL, y= "ICC value")+
  scale_color_brewer(palette = "Set2") +
  scale_x_discrete(labels = "")+
  theme_minimal()+
  geom_point(size = 1, position=position_jitter(w=0.8))
plot <- ggplotly(plot, tooltip="text")
plot

ICC_data <- ICC_data %>% 
  pivot_longer(cols = everything()) %>% 
  mutate(reliability = case_when(
    value < 0.5 ~ "poor",
    value >= 0.5 &
      value < 0.75 ~ "moderate",
    value >= 0.75 &
      value < 0.9 ~ "good",
    value >= 0.9 ~ "excellent"
  )) %>% arrange(desc(value))
ICC_data
```
<br>

## Put together

ICC and CCC values are similar : ICC is more tolerant in its classification of "excelent" (0.90 vs 0.95 for CCC).  
The following table is saved at   
smb://hlm/data/project/Peres_Research/Ovarian - Radiomics/Christelle/stable features/concordance CCC and ICC.csv
```{r concordance}
concordance <- full_join(CCC_data, ICC_data, by = "name", suffix = c("_CCC", "_ICC")) %>% arrange(desc(value_ICC)) %>% 
  select(value_ICC, reliability_ICC, value_CCC, reliability_CCC, name)
concordance
# write_csv(concordance, paste0(path, "/stable features/concordance CCC and ICC.csv"))
```
<br>

***

# `r NROW(concordance %>% filter(value_CCC >= 0.95) %>% select(feature = name))` Stable Features with CCC ≥ 0.95
<font size="10"> `r  emo::ji("party_popper")``r  emo::ji("balloon")``r  emo::ji("clinking_glasses")``r  emo::ji("confetti")`</font> 
```{r, rows.print=75}
concordance %>% filter(value_CCC >= 0.95) %>% select(feature = name)
```

```{r}
concordance <- data.frame(namee = c("f1statistical_m", "f2statistical_v", "f16statistical_",
                                    "f37intensity_hi", "f41minimum_hist", "f59centre_of_ma", 
                                    "f65flatness", "f80com_x_pxl", "f81com_y_pxl", "f82com_z_pxl",
                                    "f83com_x_mm", 'f85com_z_mm', 'f87weighted_com', 'f109avgcoocurre', 
                                    "f110avgcoocurre", "f113avgcoocurre", "f117avg_3d_sre_", "f139glszm_large",
                                    "f144glszm_zone_"))
# write_rds(concordance, "concordance.rds")
```


